---
title: "BioInformedControlRule-CurrentRegstoTarget"
author: "Kamran Walsh"
date: "2024-04-16"
output: html_document
---

Code for testing recmeasures with option of selecting different HCRs (Percent Change Approach, Biological Reference Point, Biomass-Based Matrix) with different regulation types held constant.

```{r}
setwd("/Users/kam-macpro/Desktop/FlounderMSE")
fluke <- readRDS("/Users/kam-macpro/Desktop/FlounderMSE/state_lookup.rds")
#View(fluke)

library(dplyr)
library(tidyr)
library(data.table)
flukecatch <- tibble(fluke)
```

Inputs - Enter Current Regulations and Control Rule to be Tested
```{r}
#Regs
state = "NY"
bag = 4
minlen = 18.5
seasonlen = 162

#Control Rule
Alternative = "Table1"
#Table 1 = Percent Change Approach
#Table 2 = Biological Reference Point Approach
#Table 3 = Biomass Based Matrix Approach
#Table 4 = Overfishing Based Matrix Approach 
```

Determine Expected Catch Given Current Regulations from Lookup Table:
```{r}
functioncatch_commonreg <- function(flukecatch, State, Bag, MinLen, SeasonLen){
  flukecatch %>%
    group_by(State) %>%
    filter(
      Bag == bag,
      MinLen == minlen,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])
    )
}
catchallstates_commonreg <- functioncatch_commonreg(flukecatch, State, land)
catchallstates_commonreg
```

Use GAM to extract CIs:
```{r}

len <- seq(10,28)
states <- c("DE", "MD", "NJ", "NY", "VA", "CT", "MA", "RI", "NC")
waves <- 2:6
Bag <- bag 
MinLen <- minlen
SeasLen <- catchallstates_commonreg$SeasonLen[1]

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = states,
                           Length = len, #what does this mean
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
library(mgcv)
gamland <- readRDS("gam_land.rds")  
summary(gamland)
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#lognormal CI 
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

outputland <- sum(output2$fit)
outputland

#CIs
upperCI_test <- sum(output2$upr)
upperCI_test
lowerCI_test <- sum(output2$lwr)
lowerCI_test

#Rec demand model expected harvest, sd, CV
#harvestrecdemand <- 8826699
#sdrecdemand <- 530839
#CVrecdemand <- 0.06

#upperCI_test/outputland
#lowerCI_test/outputland

#from randomly trying a few different starting regulations, upperCI_test/outputland varies from ~1.2 - ~1.55, lowerCI_test/outputland varies from ~0.4 - ~0.75.
```

Control Rules:

Percent Change Approach Bin Structure:
```{r}
# Inputs 
# For now I just left all of the relevant inputs in each chunk
RHL <- 6350000 # I just pulled this RHL value off the internet for now
expectedharvest <- sum(catchallstates_commonreg$land) 
upperCI <- upperCI_test
lowerCI <- lowerCI_test
BBMSY = 1.5 

 if (Alternative == "Table1"){
#1.1
if(RHL > upperCI & BBMSY >= 1.5){x <- abs(((RHL-expectedharvest)/expectedharvest)+1); if(x > 1.4){x <- 1.4}}
  
#1.2
if(RHL > upperCI & BBMSY >= 1 & BBMSY < 1.5){x <- abs(((RHL-expectedharvest)/expectedharvest)+1); if(x > 1.2){x <- 1.2}}
  
#1.3
if(RHL > upperCI & BBMSY < 1){x <- 1.1}
  
#2.1 
if(between(RHL, lowerCI, upperCI) & BBMSY >= 1.5){x <- 1.1} 
  
#2.2
if(between(RHL, lowerCI, upperCI) & BBMSY >= 1 & BBMSY < 1.5){x <- 1} 
  
#2.3
if(between(RHL, lowerCI, upperCI) & BBMSY < 1){x <- 0.9} 
  
#3.1
if(RHL < lowerCI & BBMSY >= 1.5){x <- 0.9} 
  
#3.2
if(RHL < lowerCI & BBMSY >= 1 & BBMSY < 1.5){x <- 1-abs((RHL-expectedharvest)/expectedharvest); if(x < 0.8){x <- 0.8}} 
  
#3.3
if(RHL < lowerCI & BBMSY < 1){x <- 1-abs((RHL-expectedharvest)/expectedharvest); if(x < 0.6){x <- 0.6}} 

   # calculates target catch based off of degree of liberalization/reduction
catchallstates_commonreg_HCR <- catchallstates_commonreg
catchallstates_commonreg_HCR$land <- x*catchallstates_commonreg_HCR$land
catchallstates_commonreg_HCR
}
```
Biological Reference Point Approach
```{r}
#Biological Info
#Not sure what the relevant Rec and Biomass data/parameters are supposed to look like

Rpresent = 1 # High recruitment is greater than or equal to median, low is less than 
Rmedian = 1.1 
Bpresent = 1
Bpast = 1.1
BBMSY = 0.5
F = 1.1
FMSY = 1

#Fishery Metrics
RHL = 6350000
upperCI = upperCI_test 
lowerCI = lowerCI_test 

#Reduction/Liberalization Measures
liberal = 1.1
initial = 1
restrictive = 0.9
veryrestrictive = 0.8


if(Alternative == "Table2"){

  #MORTALITY
if(F > FMSY){Overfishing = "yes"}
if(F <= FMSY){Overfishing = "no"}
  
  #RECTREND
if(Rpresent >= Rmedian){R = "high"}
if(Rpresent < Rmedian){R = "low"}
  
  #BIOTREND
  # not sure if this is the correct interpretation of the biomass trend specifications 
  
#if(Bpresent < (Bpast*(1+0.04)) & Bpresent > (Bpast*(1-0.04))){B = "Increasing"} #stable
if(Bpresent > (Bpast*(1-0.04))){B = "Increasing"}
if(Bpresent <= (Bpast*(1-0.04))){B = "Decreasing"}
  
#BIOMASS IS VERY HIGH 

    #Overfishing not occurring
if(BBMSY >= 1.5 & Overfishing == "no" & B == "Increasing"){x <- liberal}
if(BBMSY >= 1.5 & Overfishing == "no" & B == "Decreasing"){x <- initial}

    #Overfishing is occurring
#RHL not exceeded
if(BBMSY >= 1.5 & Overfishing == "yes" & RHL >= lowerCI & B == "Increasing" & R == "high"){x <- initial}
if(BBMSY >= 1.5 & Overfishing == "yes" & RHL >= lowerCI & B == "Increasing" & R == "low"){x <- restrictive}  
if(BBMSY >= 1.5 & Overfishing == "yes" & RHL >= lowerCI & B == "Decreasing"){x <- restrictive}
#RHL exceeded
if(BBMSY >= 1.5 & Overfishing == "yes" & RHL < lowerCI){x <- restrictive}

        # I made harvest not exceeded RHL >= lowerCI instead of RHL > lowerCI to not break it in the             # unlikely event the RHL and CI bounds perfectly equal one another 
  
#BIOMASS IS HIGH 

    #Overfishing not occurring
if(BBMSY >= 1 & BBMSY < 1.5 & Overfishing == "no" & B == "Increasing"){x <- liberal}
if(BBMSY >= 1 & BBMSY < 1.5 & Overfishing == "no" & B == "Decreasing"){x <- initial}

    #Overfishing is occurring 
#RHL not exceeded
if(BBMSY >= 1 & BBMSY < 1.5 & Overfishing == "yes" & RHL >= lowerCI & B == "Increasing" & R == "high"){x <- initial}
if(BBMSY >= 1 & BBMSY < 1.5 & Overfishing == "yes" & RHL >= lowerCI & B == "Increasing" & R == "low"){x <- restrictive}
if(BBMSY >= 1 & BBMSY < 1.5 & Overfishing == "yes" & RHL >= lowerCI & B == "Decreasing"){x <- restrictive}
#RHL exceeded
if(BBMSY >= 1 & BBMSY < 1.5 & Overfishing == "yes" & RHL < lowerCI){x <- restrictive}
    
#BIOMASS IS LOW

    #Overfishing not occurring
if(BBMSY < 1 & BBMSY >= 0.5 & Overfishing == "no" & B == "Increasing" & R == "high"){x <- initial}
if(BBMSY < 1 & BBMSY >= 0.5 & Overfishing == "no" & B == "Increasing" & R == "low"){x <- restrictive}
if(BBMSY < 1 & BBMSY >= 0.5 & Overfishing == "no" & B == "Decreasing"){x <- restrictive}

    #Overfishing is occurring
#RHL not exceeded
if(BBMSY < 1 & BBMSY >= 0.5 & Overfishing == "yes" & RHL >= lowerCI & B == "Increasing" & R == "high"){x <- initial}
  if(BBMSY < 1 & BBMSY >= 0.5 & Overfishing == "yes" & RHL >= lowerCI & B == "Increasing" & R == "low"){x <- restrictive}
if(BBMSY < 1 & BBMSY >= 0.5 & Overfishing == "yes" & RHL >= lowerCI & B == "Decreasing"){x <- restrictive}
#RHL exceeded
if(BBMSY < 1 & BBMSY >= 0.5 & Overfishing == "yes" & RHL < lowerCI){x <- restrictive}

#OVERFISHED 
if(BBMSY < 0.5){x <- veryrestrictive}

  # calculates target catch based off of degree of liberalization/reduction
catchallstates_commonreg_HCR <- catchallstates_commonreg
catchallstates_commonreg_HCR$land <- x*catchallstates_commonreg_HCR$land
catchallstates_commonreg_HCR
}
```

Biomass Based Matrix Approach
```{r}

#Liberalization/Reduction Measures
Bin1 <- 1.4
Bin2 <- 1.2
Bin3 <- 1.1
Bin4 <- 0.9
Bin5 <- 0.8
Bin6 <- 0.6

if(Alternative=="Table3"){

  # same thing here as in biological reference point approach; not sure if this is correct
if(Bpresent < (Bpast*(1+0.04)) & Bpresent > (Bpast*(1-0.04))){B = "Decreasing"} #stable
if(Bpresent >= (Bpast*(1+0.04))){B = "Increasing"}
if(Bpresent <= (Bpast*(1-0.04))){B = "Decreasing"}
  
if(BBMSY >= 1.5){x <- Bin1}
if(BBMSY < 1.5 & BBMSY >= 1 & B == "Increasing"){x <- Bin1}
if(BBMSY < 1.5 & BBMSY >= 1 & B == "Decreasing"){x <- Bin2}
if(BBMSY < 1 & BBMSY >= 0.5 & B == "Increasing"){x <- Bin3}
if(BBMSY < 1 & BBMSY >= 0.5 & B == "Decreasing"){x <- Bin4}
if(BBMSY < 0.5 & B == "Increasing"){x <- Bin5}
if(BBMSY < 0.5 & B == "Decreasing"){x <- Bin6}

  # calculates target catch based off of degree of liberalization/reduction
catchallstates_commonreg_HCR <- catchallstates_commonreg
catchallstates_commonreg_HCR$land <- x*catchallstates_commonreg_HCR$land
catchallstates_commonreg_HCR
}

```

Overfishing Based Matrix Approach
```{r}

#Liberalization/Reduction Measures
Bin1 <- 1.4
Bin2 <- 1.2
Bin3 <- 1.1
Bin4 <- 1
Bin5 <- 0.9
Bin6 <- 0.8
Bin7 <- 0.6

if(Alternative=="Table4"){

if(F > FMSY){Overfishing = "yes"}
if(F <= FMSY){Overfishing = "no"}

if(BBMSY >= 1.5 & Overfishing == "no"){x <- Bin1}
if(BBMSY >= 1.5 & Overfishing == "yes"){x <- Bin4}
if(BBMSY < 1.5 & BBMSY >= 1 & Overfishing == "no"){x <- Bin2}
if(BBMSY < 1.5 & BBMSY >= 1 & Overfishing == "yes"){x <- Bin5}
if(BBMSY < 1 & BBMSY >= 0.5 & Overfishing == "no"){x <- Bin3}
if(BBMSY < 1 & BBMSY >= 0.5 & Overfishing == "yes"){x <- Bin6}
if(BBMSY < 0.5){x <- Bin7}

  # calculates target catch based off of degree of liberalization/reduction
catchallstates_commonreg_HCR <- catchallstates_commonreg
catchallstates_commonreg_HCR$land <- x*catchallstates_commonreg_HCR$land
catchallstates_commonreg_HCR
}

```

Lookup Expected Catch/Discards + Return Regs: 

Season Length Change:
```{r}
NCcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="NC"]
DEcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="DE"]
MAcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="MA"]
RIcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="RI"]
NYcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="NY"]
MDcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="MD"]
CTcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="CT"]
VAcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="VA"]
NJcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="NJ"]

# North Carolina

#find next lowest value in lookup table
functioncatchNC_seasonlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="NC") %>% 
    filter(
      State=="NC",
      Bag == bag,
      MinLen == minlen) %>%
   filter(
   land == max(land[land <= NCcatch_common])) 
}
NC_seasonlen <- functioncatchNC_seasonlen(flukecatch, State, land)
NC_seasonlen <- NC_seasonlen %>% mutate(TargetMet = "TRUE")

#return higher value if no lower value exists given constraints
NC_if <- function(flukecatch, State, land){if(nrow(NC_seasonlen)==0){
    flukecatch %>% 
    group_by(State=="NC") %>% 
    filter(
      State=="NC",
      Bag == bag,
      MinLen == minlen) %>%
    filter(abs(land - NCcatch_common) == min(abs(land - NCcatch_common)))
}
}
NC_seasonlen2 <- NC_if(flukecatch, State, land)

#Delaware
functioncatchDE_seasonlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="DE") %>% 
    filter(
      State=="DE",
      Bag == bag,
      MinLen == minlen) %>%
   filter(
   land == max(land[land <= DEcatch_common])) 
}
DE_seasonlen <- functioncatchDE_seasonlen(flukecatch, State, land)
DE_seasonlen <- DE_seasonlen %>% mutate(TargetMet = "TRUE")


DE_if <- function(flukecatch, State, land){if(nrow(DE_seasonlen)==0){
    flukecatch %>% 
    group_by(State=="DE") %>% 
    filter(
      State=="DE",
      Bag == bag,
      MinLen == minlen) %>%
    filter(abs(land - DEcatch_common) == min(abs(land - DEcatch_common)))
}
}
DE_seasonlen2 <- DE_if(flukecatch, State, land)

#Massachusetts
functioncatchMA_seasonlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="MA") %>% 
    filter(
      State=="MA",
      Bag == bag,
      MinLen == minlen) %>%
   filter(
   land == max(land[land <= MAcatch_common])) 
}
MA_seasonlen <- functioncatchMA_seasonlen(flukecatch, State, land)
MA_seasonlen <- MA_seasonlen %>% mutate(TargetMet = "TRUE")

MA_if <- function(flukecatch, State, land){if(nrow(MA_seasonlen)==0){
    flukecatch %>% 
    group_by(State=="MA") %>% 
    filter(
      State=="MA",
      Bag == bag,
      MinLen == minlen) %>%
    filter(abs(land - MAcatch_common) == min(abs(land - MAcatch_common)))
}
}
MA_seasonlen2 <- MA_if(flukecatch, State, land)

#Rhode Island
functioncatchRI_seasonlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="RI") %>% 
    filter(
      State=="RI",
      Bag == bag,
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= RIcatch_common]))
}
RI_seasonlen <- functioncatchRI_seasonlen(flukecatch, State, land)
RI_seasonlen <- RI_seasonlen %>% mutate(TargetMet = "TRUE")

RI_if <- function(flukecatch, State, land){if(nrow(RI_seasonlen)==0){
    flukecatch %>% 
    group_by(State=="RI") %>% 
    filter(
      State=="RI",
      Bag == bag,
      MinLen == minlen) %>%
    filter(abs(land - RIcatch_common) == min(abs(land - RIcatch_common)))
}
}
RI_seasonlen2 <- RI_if(flukecatch, State, land)

#New York
functioncatchNY_seasonlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="NY") %>% 
    filter(
      State=="NY",
      Bag == bag,
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= NYcatch_common]))
}
NY_seasonlen <- functioncatchNY_seasonlen(flukecatch, State, land)
NY_seasonlen <- NY_seasonlen %>% mutate(TargetMet = "TRUE")

NY_if <- function(flukecatch, State, land){if(nrow(NY_seasonlen)==0){
    flukecatch %>% 
    group_by(State=="NY") %>% 
    filter(
      State=="NY",
      Bag == bag,
      MinLen == minlen) %>%
    filter(abs(land - NYcatch_common) == min(abs(land - NYcatch_common)))
}
}
NY_seasonlen2 <- NY_if(flukecatch, State, land)

#Maryland
functioncatchMD_seasonlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="MD") %>% 
    filter(
      State=="MD",
      Bag == bag,
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= MDcatch_common]))
}
MD_seasonlen <- functioncatchMD_seasonlen(flukecatch, State, land)
MD_seasonlen <- MD_seasonlen %>% mutate(TargetMet = "TRUE")

MD_if <- function(flukecatch, State, land){if(nrow(MD_seasonlen)==0){
    flukecatch %>% 
    group_by(State=="MD") %>% 
    filter(
      State=="MD",
      Bag == bag,
      MinLen == minlen) %>%
    filter(abs(land - MDcatch_common) == min(abs(land - MDcatch_common)))
}
}
MD_seasonlen2 <- MD_if(flukecatch, State, land)

#Connecticut 
functioncatchCT_seasonlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="CT") %>% 
    filter(
      State=="CT",
      Bag == bag,
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= CTcatch_common]))
}
CT_seasonlen <- functioncatchCT_seasonlen(flukecatch, State, land)
CT_seasonlen <- CT_seasonlen %>% mutate(TargetMet = "TRUE")

CT_if <- function(flukecatch, State, land){if(nrow(CT_seasonlen)==0){
    flukecatch %>% 
    group_by(State=="CT") %>% 
    filter(
      State=="CT",
      Bag == bag,
      MinLen == minlen) %>%
    filter(abs(land - CTcatch_common) == min(abs(land - CTcatch_common)))
}
}
CT_seasonlen2 <- CT_if(flukecatch, State, land)

#Virginia
functioncatchVA_seasonlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="VA") %>% 
    filter(
      State=="VA",
      Bag == bag,
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= VAcatch_common]))
}
VA_seasonlen <- functioncatchVA_seasonlen(flukecatch, State, land)
VA_seasonlen <- VA_seasonlen %>% mutate(TargetMet = "TRUE")

VA_if <- function(flukecatch, State, land){if(nrow(VA_seasonlen)==0){
    flukecatch %>% 
    group_by(State=="VA") %>% 
    filter(
      State=="VA",
      Bag == bag,
      MinLen == minlen) %>%
    filter(abs(land - VAcatch_common) == min(abs(land - VAcatch_common)))
}
}
VA_seasonlen2 <- VA_if(flukecatch, State, land)

# New Jersey 
functioncatchNJ_seasonlen<- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="NJ") %>% 
    filter(
      State=="NJ",
      Bag == bag,
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= NJcatch_common]))
}
NJ_seasonlen <- functioncatchNJ_seasonlen(flukecatch, State, land)
NJ_seasonlen <- NJ_seasonlen %>% mutate(TargetMet = "TRUE")

NJ_if <- function(flukecatch, State, land){if(nrow(NJ_seasonlen)==0){
    flukecatch %>% 
    group_by(State=="NJ") %>% 
    filter(
      State=="NJ",
      Bag == bag,
      MinLen == minlen) %>%
    filter(abs(land - NJcatch_common) == min(abs(land - NJcatch_common)))
}
}
NJ_seasonlen2 <- NJ_if(flukecatch, State, land)

if(nrow(NC_seasonlen)==0){NC_seasonlen <- NC_seasonlen2 %>%  mutate(TargetMet = "FALSE")}
if(nrow(DE_seasonlen)==0){DE_seasonlen <- DE_seasonlen2 %>%  mutate(TargetMet = "FALSE")}
if(nrow(MA_seasonlen)==0){MA_seasonlen <- MA_seasonlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(RI_seasonlen)==0){RI_seasonlen <- RI_seasonlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(NY_seasonlen)==0){NY_seasonlen <- NY_seasonlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(NJ_seasonlen)==0){NJ_seasonlen <- NJ_seasonlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(MD_seasonlen)==0){MD_seasonlen <- MD_seasonlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(CT_seasonlen)==0){CT_seasonlen <- CT_seasonlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(VA_seasonlen)==0){VA_seasonlen <- VA_seasonlen2 %>% mutate(TargetMet = "FALSE")}

targetcatchregs_seasonlen <- list(NC_seasonlen, VA_seasonlen, MD_seasonlen, DE_seasonlen, NJ_seasonlen, NY_seasonlen, CT_seasonlen, RI_seasonlen, MA_seasonlen)
targetcatchregs_seasonlen_ <- rbindlist(targetcatchregs_seasonlen, fill = TRUE, )
targetcatchregs_seasonlen_ = subset(targetcatchregs_seasonlen_, select = c(State, Bag, MinLen, SeasonLen, land, disc, TargetMet))
targetcatchregs_seasonlen_
```

Size Limit Change:
```{r}
NCcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="NC"]
DEcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="DE"]
MAcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="MA"]
RIcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="RI"]
NYcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="NY"]
MDcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="MD"]
CTcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="CT"]
VAcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="VA"]
NJcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="NJ"]

#North Carolina
functioncatchNC_common_minlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="NC") %>% 
    filter(
      State=="NC",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(
      land == max(land[land <= NCcatch_common]))
}
NC_common_minlen <- functioncatchNC_common_minlen(flukecatch, State, land)
NC_common_minlen <- NC_common_minlen %>% mutate(TargetMet = "TRUE")

NC_if_minlen <- function(flukecatch, State, land){if(nrow(NC_common_minlen)==0){
    flukecatch %>% 
    group_by(State=="NC") %>% 
    filter(
      State=="NC",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(abs(land - NCcatch_common) == min(abs(land - NCcatch_common)))
}
}
NC_common_minlen2 <- NC_if_minlen(flukecatch, State, land)

#Delaware
functioncatchDE_common_minlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="DE") %>% 
    filter(
      State =="DE",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(
      land == max(land[land <= DEcatch_common]))
}
DE_common_minlen <- functioncatchDE_common_minlen(flukecatch, State, land)
DE_common_minlen <- DE_common_minlen %>% mutate(TargetMet = "TRUE")

DE_if_minlen <- function(flukecatch, State, land){if(nrow(DE_common_minlen)==0){
    flukecatch %>% 
    group_by(State=="DE") %>% 
    filter(
      State=="DE",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(abs(land - DEcatch_common) == min(abs(land - DEcatch_common)))
}
}
DE_common_minlen2 <- DE_if_minlen(flukecatch, State, land)

#Massachusetts
functioncatchMA_common_minlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="MA") %>% 
    filter(
      State=="MA",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(
      land == max(land[land <= MAcatch_common]))
}
MA_common_minlen <- functioncatchMA_common_minlen(flukecatch, State, land)
MA_common_minlen <- MA_common_minlen %>% mutate(TargetMet = "TRUE")

MA_if_minlen <- function(flukecatch, State, land){if(nrow(MA_common_minlen)==0){
    flukecatch %>% 
    group_by(State=="MA") %>% 
    filter(
      State=="MA",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(abs(land - MAcatch_common) == min(abs(land - MAcatch_common)))
}
}
MA_common_minlen2 <- MA_if_minlen(flukecatch, State, land)

#Rhode Island
functioncatchRI_common_minlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="RI") %>% 
    filter(
      State=="RI",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(
      land == max(land[land <= RIcatch_common]))
}
RI_common_minlen <- functioncatchRI_common_minlen(flukecatch, State, land)
RI_common_minlen <- RI_common_minlen %>% mutate(TargetMet = "TRUE")

RI_if_minlen <- function(flukecatch, State, land){if(nrow(RI_common_minlen)==0){
    flukecatch %>% 
    group_by(State=="RI") %>% 
    filter(
      State=="RI",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(abs(land - RIcatch_common) == min(abs(land - RIcatch_common)))
}
}
RI_common_minlen2 <- RI_if_minlen(flukecatch, State, land)

#New York
functioncatchNY_common_minlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="NY") %>% 
    filter(
      State=="NY",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(
      land == max(land[land <= NYcatch_common]))
}
NY_common_minlen <- functioncatchNY_common_minlen(flukecatch, State, land)
NY_common_minlen <- NY_common_minlen %>% mutate(TargetMet = "TRUE")

NY_if_minlen <- function(flukecatch, State, land){if(nrow(NY_common_minlen)==0){
    flukecatch %>% 
    group_by(State=="NY") %>% 
    filter(
      State=="NY",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(abs(land - NYcatch_common) == min(abs(land - NYcatch_common)))
}
}
NY_common_minlen2 <- NY_if_minlen(flukecatch, State, land)

#Maryland
functioncatchMD_common_minlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="MD") %>% 
    filter(
      State=="MD",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(
      land == max(land[land <= MDcatch_common]))
}
MD_common_minlen <- functioncatchMD_common_minlen(flukecatch, State, land)
MD_common_minlen <- MD_common_minlen %>% mutate(TargetMet = "TRUE")

MD_if_minlen <- function(flukecatch, State, land){if(nrow(MD_common_minlen)==0){
    flukecatch %>% 
    group_by(State=="MD") %>% 
    filter(
      State=="MD",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(abs(land - MDcatch_common) == min(abs(land - MDcatch_common)))
}
}
MD_common_minlen2 <- MD_if_minlen(flukecatch, State, land)

#Connecticut
functioncatchCT_common_minlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="CT") %>% 
    filter(
      State=="CT",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(
      land == max(land[land <= CTcatch_common]))
}
CT_common_minlen <- functioncatchCT_common_minlen(flukecatch, State, land)
CT_common_minlen <- CT_common_minlen %>% mutate(TargetMet = "TRUE")

CT_if_minlen <- function(flukecatch, State, land){if(nrow(CT_common_minlen)==0){
    flukecatch %>% 
    group_by(State=="CT") %>% 
    filter(
      State=="CT",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(abs(land - CTcatch_common) == min(abs(land - CTcatch_common)))
}
}
CT_common_minlen2 <- CT_if_minlen(flukecatch, State, land)

#Virginia
functioncatchVA_common_minlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="VA") %>% 
    filter(
      State=="VA",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(
      land == max(land[land <= VAcatch_common]))
}
VA_common_minlen <- functioncatchVA_common_minlen(flukecatch, State, land)
VA_common_minlen <- VA_common_minlen %>% mutate(TargetMet = "TRUE")

VA_if_minlen <- function(flukecatch, State, land){if(nrow(VA_common_minlen)==0){
    flukecatch %>% 
    group_by(State=="VA") %>% 
    filter(
      State=="VA",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(abs(land - VAcatch_common) == min(abs(land - VAcatch_common)))
}
}
VA_common_minlen2 <- VA_if_minlen(flukecatch, State, land)

#New Jersey
functioncatchNJ_common_minlen <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="NJ") %>% 
    filter(
      State=="NJ",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(
      land == max(land[land <= NJcatch_common]))
}
NJ_common_minlen <- functioncatchNJ_common_minlen(flukecatch, State, land)
NJ_common_minlen <- NJ_common_minlen %>% mutate(TargetMet = "TRUE")

NJ_if_minlen <- function(flukecatch, State, land){if(nrow(NJ_common_minlen)==0){
    flukecatch %>% 
    group_by(State=="NJ") %>% 
    filter(
      State=="NJ",
      Bag == bag,
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen])) %>%
    filter(abs(land - NJcatch_common) == min(abs(land - NJcatch_common)))
}
}
NJ_common_minlen2 <- NJ_if_minlen(flukecatch, State, land)

if(nrow(NC_common_minlen)==0){NC_common_minlen <- NC_common_minlen2 %>%  mutate(TargetMet = "FALSE")}
if(nrow(DE_common_minlen)==0){DE_common_minlen <- DE_common_minlen2 %>%  mutate(TargetMet = "FALSE")}
if(nrow(MA_common_minlen)==0){MA_common_minlen <- MA_common_minlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(RI_common_minlen)==0){RI_common_minlen <- RI_common_minlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(NY_common_minlen)==0){NY_common_minlen <- NY_common_minlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(NJ_common_minlen)==0){NJ_common_minlen <- NJ_common_minlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(MD_common_minlen)==0){MD_common_minlen <- MD_common_minlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(CT_common_minlen)==0){CT_common_minlen <- CT_common_minlen2 %>% mutate(TargetMet = "FALSE")}
if(nrow(VA_common_minlen)==0){VA_common_minlen <- VA_common_minlen2 %>% mutate(TargetMet = "FALSE")}

targetcatchregs_common_minlen <- list(NC_common_minlen, VA_common_minlen, MD_common_minlen, DE_common_minlen, NJ_common_minlen, NY_common_minlen, CT_common_minlen, RI_common_minlen, MA_common_minlen)
targetcatchregs_common_minlen_ <- rbindlist(targetcatchregs_common_minlen, fill = TRUE, )
targetcatchregs_common_minlen_ = subset(targetcatchregs_common_minlen_, select = c(State, Bag, MinLen, SeasonLen, land, disc, TargetMet))
targetcatchregs_common_minlen_
```
Bag Limit Change:
```{r}
NCcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="NC"]
DEcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="DE"]
MAcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="MA"]
RIcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="RI"]
NYcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="NY"]
MDcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="MD"]
CTcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="CT"]
VAcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="VA"]
NJcatch_common <- catchallstates_commonreg_HCR$land[catchallstates_commonreg$State=="NJ"]

#North Carolina
functioncatchNC_common <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="NC") %>% 
    filter(
      State=="NC",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= NCcatch_common]))
}
NC_common <- functioncatchNC_common(flukecatch, State, land)
NC_common <- NC_common %>% mutate(TargetMet = "TRUE")

NC_if_common <- function(flukecatch, State, land){if(nrow(NC_common)==0){
    flukecatch %>% 
    group_by(State=="NC") %>% 
    filter(
      State=="NC",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(abs(land - NCcatch_common) == min(abs(land - NCcatch_common)))
}
}
NC_common2 <- NC_if_common(flukecatch, State, land)

#Delaware
functioncatchDE_common <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="DE") %>% 
    filter(
      State =="DE",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= DEcatch_common]))
}
DE_common <- functioncatchDE_common(flukecatch, State, land)
DE_common <- DE_common %>% mutate(TargetMet = "TRUE")

DE_if_common <- function(flukecatch, State, land){if(nrow(DE_common)==0){
    flukecatch %>% 
    group_by(State=="DE") %>% 
    filter(
      State=="DE",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(abs(land - DEcatch_common) == min(abs(land - DEcatch_common)))
}
}
DE_common2 <- DE_if_common(flukecatch, State, land)

#Massachusetts
functioncatchMA_common <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="MA") %>% 
    filter(
      State=="MA",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= MAcatch_common]))
}
MA_common <- functioncatchMA_common(flukecatch, State, land)
MA_common <- MA_common %>% mutate(TargetMet = "TRUE")

MA_if_common <- function(flukecatch, State, land){if(nrow(MA_common)==0){
    flukecatch %>% 
    group_by(State=="MA") %>% 
    filter(
      State=="MA",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(abs(land - MAcatch_common) == min(abs(land - MAcatch_common)))
}
}
MA_common2 <- MA_if_common(flukecatch, State, land)

#Rhode Island
functioncatchRI_common <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="RI") %>% 
    filter(
      State=="RI",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= RIcatch_common]))
}
RI_common <- functioncatchRI_common(flukecatch, State, land)
RI_common <- RI_common %>% mutate(TargetMet = "TRUE")

RI_if_common <- function(flukecatch, State, land){if(nrow(RI_common)==0){
    flukecatch %>% 
    group_by(State=="RI") %>% 
    filter(
      State=="RI",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(abs(land - RIcatch_common) == min(abs(land - RIcatch_common)))
}
}
RI_common2 <- RI_if_common(flukecatch, State, land)

#New York
functioncatchNY_common <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="NY") %>% 
    filter(
      State=="NY",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= NYcatch_common]))
}
NY_common <- functioncatchNY_common(flukecatch, State, land)
NY_common <- NY_common %>% mutate(TargetMet = "TRUE")

NY_if_common <- function(flukecatch, State, land){if(nrow(NY_common)==0){
    flukecatch %>% 
    group_by(State=="NY") %>% 
    filter(
      State=="NY",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(abs(land - NYcatch_common) == min(abs(land - NYcatch_common)))
}
}
NY_common2 <- NY_if_common(flukecatch, State, land)

#Maryland
functioncatchMD_common <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="MD") %>% 
    filter(
      State=="MD",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= MDcatch_common]))
}
MD_common <- functioncatchMD_common(flukecatch, State, land)
MD_common <- MD_common %>% mutate(TargetMet = "TRUE")

MD_if_common <- function(flukecatch, State, land){if(nrow(MD_common)==0){
    flukecatch %>% 
    group_by(State=="MD") %>% 
    filter(
      State=="MD",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(abs(land - MDcatch_common) == min(abs(land - MDcatch_common)))
}
}
MD_common2 <- MD_if_common(flukecatch, State, land)

#Connecticut
functioncatchCT_common <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="CT") %>% 
    filter(
      State=="CT",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= CTcatch_common]))
}
CT_common <- functioncatchCT_common(flukecatch, State, land)
CT_common <- CT_common %>% mutate(TargetMet = "TRUE")

CT_if_common <- function(flukecatch, State, land){if(nrow(CT_common)==0){
    flukecatch %>% 
    group_by(State=="CT") %>% 
    filter(
      State=="CT",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(abs(land - CTcatch_common) == min(abs(land - CTcatch_common)))
}
}
CT_common2 <- CT_if_common(flukecatch, State, land)

#Virginia
functioncatchVA_common <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="VA") %>% 
    filter(
      State=="VA",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= VAcatch_common]))
}
VA_common <- functioncatchVA_common(flukecatch, State, land)
VA_common <- VA_common %>% mutate(TargetMet = "TRUE")

VA_if_common <- function(flukecatch, State, land){if(nrow(VA_common)==0){
    flukecatch %>% 
    group_by(State=="VA") %>% 
    filter(
      State=="VA",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(abs(land - VAcatch_common) == min(abs(land - VAcatch_common)))
}
}
VA_common2 <- VA_if_common(flukecatch, State, land)

#New Jersey
functioncatchNJ_common <- function(flukecatch, State, land){
  flukecatch %>% 
    group_by(State=="NJ") %>% 
    filter(
      State=="NJ",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(
      land == max(land[land <= NJcatch_common]))
}
NJ_common <- functioncatchNJ_common(flukecatch, State, land)
NJ_common <- NJ_common %>% mutate(TargetMet = "TRUE")

NJ_if_common <- function(flukecatch, State, land){if(nrow(NJ_common)==0){
    flukecatch %>% 
    group_by(State=="NJ") %>% 
    filter(
      State=="NJ",
      SeasonLen == max(SeasonLen[SeasonLen <= seasonlen]),
      MinLen == minlen) %>%
    filter(abs(land - NJcatch_common) == min(abs(land - NJcatch_common)))
}
}
NJ_common2 <- NJ_if_common(flukecatch, State, land)

if(nrow(NC_common)==0){NC_common <- NC_common2 %>%  mutate(TargetMet = "FALSE")}
if(nrow(DE_common)==0){DE_common <- DE_common2 %>%  mutate(TargetMet = "FALSE")}
if(nrow(MA_common)==0){MA_common <- MA_common2 %>% mutate(TargetMet = "FALSE")}
if(nrow(RI_common)==0){RI_common <- RI_common2 %>% mutate(TargetMet = "FALSE")}
if(nrow(NY_common)==0){NY_common <- NY_common2 %>% mutate(TargetMet = "FALSE")}
if(nrow(NJ_common)==0){NJ_common <- NJ_common2 %>% mutate(TargetMet = "FALSE")}
if(nrow(MD_common)==0){MD_common <- MD_common2 %>% mutate(TargetMet = "FALSE")}
if(nrow(CT_common)==0){CT_common <- CT_common2 %>% mutate(TargetMet = "FALSE")}
if(nrow(VA_common)==0){VA_common <- VA_common2 %>% mutate(TargetMet = "FALSE")}

targetcatchregs_common <- list(NC_common, VA_common, MD_common, DE_common, NJ_common, NY_common, CT_common, RI_common, MA_common)
targetcatchregs_common_ <- rbindlist(targetcatchregs_common, fill = TRUE, )
targetcatchregs_common_ = subset(targetcatchregs_common_, select = c(State, Bag, MinLen, SeasonLen, land, disc, TargetMet))
targetcatchregs_common_
```
Aggregating Everything Together:
```{r}
targetcatchregstest_seasonlength1 <- data.frame(targetcatchregs_seasonlen_, "Season Change")
targetcatchregstest_minlength1 <- data.frame(targetcatchregs_common_minlen_, "Length Change")
targetcatchregstest_baglimit1 <- data.frame(targetcatchregs_common_, "Bag Change")

names(targetcatchregstest_seasonlength1)[8] = "Reg Changed"
names(targetcatchregstest_minlength1)[8] = "Reg Changed"
names(targetcatchregstest_baglimit1)[8] = "Reg Changed"

finaltable1 <- rbind(targetcatchregstest_seasonlength1, targetcatchregstest_minlength1, targetcatchregstest_baglimit1)
finaltable1

#RDS files depending on control rule selected

#Percent Change Approach
if(Alternative == "Table1"){
 #saveRDS(finaltable1, file = "PCA_BiologicallyInformed_CatchTable_NYRegs.rds")
#PCA_BioInformed_CatchTable_NYRegs <- readRDS("PCA_BiologicallyInformed_CatchTable_NYRegs.rds")
}

#Biological Reference Point Approach 
if(Alternative == "Table2"){
 #saveRDS(finaltable1, file = "BRP_BiologicallyInformed_CatchTable_NYRegs.rds")
#BRP_BioInformed_CatchTable_NYRegs <- readRDS("BRP_BiologicallyInformed_CatchTable_NYRegs.rds")
}

#Biomass Based Matrix Approach
if(Alternative == "Table3"){
 #saveRDS(finaltable1, file = "BBM_BiologicallyInformed_CatchTable_NYRegs.rds")
#BBM_BioInformed_CatchTable_NYRegs <- readRDS("BBM_BiologicallyInformed_CatchTable_NYRegs.rds")
}

#Overfishing Based Matrix Approach 
if(Alternative == "Table4"){
 #saveRDS(finaltable1, file = "OBM_BiologicallyInformed_CatchTable_NYRegs.rds")
#BBM_BioInformed_CatchTable_NYRegs <- readRDS("OBM_BiologicallyInformed_CatchTable_NYRegs.rds")
}
```
