---
title: "GAMPredictScale"
author: "Kamran Walsh"
date: "2024-04-29"
output: html_document
---

```{r}
setwd("/Users/kam-macpro/Desktop/FlounderMSE")
fluke <- readRDS("/Users/kam-macpro/Desktop/FlounderMSE/state_lookup.rds")
#View(fluke)
library(dplyr)
library(tidyr)
library(data.table)
flukecatch <- tibble(fluke)
```

```{r}

len <- seq(10,28)
#states <- c("DE", "MD", "NJ", "NY", "VA", "CT", "MA", "RI", "NC")
#waves <- 2:6
#Bag <- bag #9 calls to the gam with state constrained
#MinLen <- minlen
#SeasLen <- catchallstates_commonreg$SeasonLen[1]

```

Delaware
No option for 365 day season, did number of days fished in regulations_option1 sheet
```{r}
#Regs
len <- seq(10,28)
waves <- 2:6
Bag <- 4 #9 calls to the gam with state constrained
MinLen <- 16.5
SeasLen <-  245

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = "DE",
                           Length = len, 
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
library(mgcv)
gamland <- readRDS("gam_land.rds")  
summary(gamland)
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#fit with log(x) ~ instead of x ~

#lognormal CI
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

expectedDE <- sum(exp(output2$fit))
expectedDE

#outputland <- sum(output2$fit)
#outputland

upperCI_testDE <- sum(output2$upr)
upperCI_testDE
lowerCI_testDE <- sum(output2$lwr)
lowerCI_testDE
```


Maryland
No option for 365 day season, did number of days fished in regulations_option1 sheet
I assume no need to worry about the greater regulatory complexity, e.g. NJ, CT, and RI shore sites, NJ/DE Bay, PRFC
```{r}
#Regs
len <- seq(10,28)
waves <- 2:6
Bag <- 4 #9 calls to the gam with state constrained
MinLen <- 16.5
SeasLen <- 229

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = "MD",
                           Length = len, 
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#lognormal CI
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

expectedMD <- sum(exp(output2$fit))
expectedMD

#outputland <- sum(output2$fit)
#outputland

upperCI_testMD <- sum(output2$upr)
upperCI_testMD
lowerCI_testMD <- sum(output2$lwr)
lowerCI_testMD
```

Virginia 
No option for 365 day season, did number of days fished in regulations_option1 sheet
```{r}
#Regs
len <- seq(10,28)
waves <- 2:6
Bag <- 4 #9 calls to the gam with state constrained
MinLen <- 16.5
SeasLen <- 244

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = "VA",
                           Length = len,
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#lognormal CI
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

expectedVA <- sum(exp(output2$fit))
expectedVA

#outputland <- sum(output2$fit)
#outputland

upperCI_testVA <- sum(output2$upr)
upperCI_testVA
lowerCI_testVA <- sum(output2$lwr)
lowerCI_testVA
```

North Carolina

For here I did the open season since it allowed the GAM to produce estimates
```{r}
#Regs
len <- seq(10,28)
waves <- 2:6
Bag <- 4 #9 calls to the gam with state constrained
MinLen <- 15
SeasLen <- 235

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = "NC",
                           Length = len, 
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#lognormal CI
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

expectedNC <- sum(exp(output2$fit))
expectedNC

#outputland <- sum(output2$fit)
#outputland

upperCI_testNC <- sum(output2$upr)
upperCI_testNC
lowerCI_testNC <- sum(output2$lwr)
lowerCI_testNC
```

Massachusetts
```{r}
#Regs
len <- seq(10,28)
waves <- 2:6
Bag <- 5 #9 calls to the gam with state constrained
MinLen <- 17
SeasLen <- 140

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = "MA",
                           Length = len,
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#lognormal CI
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

expectedMA <- sum(exp(output2$fit))
expectedMA

#outputland <- sum(output2$fit)
#outputland

upperCI_testMA <- sum(output2$upr)
upperCI_testMA
lowerCI_testMA <- sum(output2$lwr)
lowerCI_testMA
```

Rhode Island 
```{r}
#Regs
len <- seq(10,28)
waves <- 2:6
Bag <- 6 #9 calls to the gam with state constrained
MinLen <- 19
SeasLen <- 243

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = "RI",
                           Length = len,
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#lognormal CI
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

expectedRI <- sum(exp(output2$fit))
expectedRI

#outputland <- sum(output2$fit)
#outputland

upperCI_testRI <- sum(output2$upr)
upperCI_testRI
lowerCI_testRI <- sum(output2$lwr)
lowerCI_testRI
```

CT
```{r}
#Regs
len <- seq(10,28)
waves <- 2:6
Bag <- 4 #9 calls to the gam with state constrained
MinLen <- 19
SeasLen <- 150

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = "CT",
                           Length = len, 
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#lognormal CI
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

expectedCT <- sum(exp(output2$fit))
expectedCT

#outputland <- sum(output2$fit)
#outputland

upperCI_testCT <- sum(output2$upr)
upperCI_testCT
lowerCI_testCT <- sum(output2$lwr)
lowerCI_testCT

```

New York 
```{r}
#Regs
len <- seq(10,28)
waves <- 2:6
Bag <- 4 #9 calls to the gam with state constrained
MinLen <- 19
SeasLen <- 150

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = "NY",
                           Length = len, 
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#lognormal CI
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

expectedNY <- sum(exp(output2$fit))
expectedNY

#outputland <- sum(output2$fit)
#outputland

upperCI_testNY <- sum(output2$upr)
upperCI_testNY
lowerCI_testNY <- sum(output2$lwr)
lowerCI_testNY

```

New Jersey
```{r}
#Regs
len <- seq(10,28)
waves <- 2:6
Bag <- 3 #9 calls to the gam with state constrained
MinLen <- 18
SeasLen <- 121

mround <- function(x,base){
  base*round(x/base)
}

wave_seasons <- data.frame(seas = seq(60,300,15),
                           w2 = c(rep(0,9),seq(15,60,15),rep(60,4)),
                           w3 = c(rep(0,1),seq(15,60,15),rep(60,12)),
                           w4 = rep(60,17),
                           w5 = c(rep(0,5),seq(15,60,15),rep(60,8)),
                           w6 = c(rep(0,13),seq(15,60,15)))
 
 dat.all <- expand.grid(State = "NJ",
                           Length = len, 
                           Bag = Bag,
                           MinLen = MinLen,
                           Wave = waves
)
dat.all$SeasonLen <- as.numeric(wave_seasons[wave_seasons$seas==as.integer(mround(as.numeric(SeasLen),15)),-1])[dat.all$Wave-1]

# dat.all$SeasonLen <- SeasonLen[dat.all$Wave-1]
gamfit <- predict.gam(gamland, newdata = dat.all, type = "link" , se.fit = TRUE)

#lognormal CI
upr <- exp(gamfit$fit + (1.96 * gamfit$se.fit))
lwr <- exp(gamfit$fit - (1.96 * gamfit$se.fit))

# Extract upper + lower CIs
output2 = cbind(dat.all, gamfit, lwr, upr)

expectedNJ <- sum(exp(output2$fit))
expectedNJ

#outputland <- sum(output2$fit)
#outputland

upperCI_testNJ <- sum(output2$upr)
upperCI_testNJ
lowerCI_testNJ <- sum(output2$lwr)
lowerCI_testNJ
```

Sum
```{r}
# Coastwide expected landings 
sumstates1 <- expectedDE + expectedMD + expectedVA + expectedNC + expectedMA + expectedRI + expectedCT + expectedNY +
expectedNJ
sumstates1

#Rec demand estimates from Lou
harvestrecdemand <- 8826699
sdrecdemand <- 530839
CVrecdemand <- 0.06

#Scaling factor

#I'm not sure if the RHL is supposed to be scaled up or down (e.g. is RHL on the scale of the rec demand or the GAM?)

SFup <- harvestrecdemand/sumstates1 
SFup

SFdown <- sumstates1/harvestrecdemand
SFdown

#Notes from meeting:
#scale the RHL from 2019 to now using scaling factor gained from comparing gam 2019 regulations predicted catch to rec demand model predicted catch 
#multiply RHL by scaling factor when comparing to CI boundaries 

```

