---
title: "Summer Flounder MSE Performance Metrics"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE,
                      warning = FALSE)
library(tidyverse)
library(ggdist)
library(scales)
library(fmsb)
library(googlesheets4)
```

_Gavin Fay_   
_(last updated: 2024-06-17)_  

<!-- #### Summary description of the results -->

<!-- Full description and interpretation of the results for the MSE can be found in the final report via the Council's [Recreational Summer Flounder MSE webpage](https://www.mafmc.org/actions/summer-flounder-mse).   -->
<!-- Operating Models: simulations were conducted for three operating models, a base-case ( __Base__), a __MRIP Bias__ scenario that conditioned the operating model assuming the MRIP estimates of recreational catch are biased high, and a distribution shift ( __Shift__) model that modeled a northward shift over time in the avaialbility of summer flounder to the recreational fishery.   -->
<!-- The performance of seven __Management Procedures__ was evaluated, which differed in the regulations settings for the recreational fishery. A summary description of the Management Procedures, and the explanation of the notation used in the plots below can be found in [this table](https://github.com/gavinfay/fluke-mafmc-recdisc/blob/main/docs/Management-Procedures-and-Metric-Descriptions.pdf).   -->
<!-- Each Management Procedure was applied to each operating model and compared using 17 __Performance Metrics__ summarizing performance associated with four Management Objectives. 100 simulations were conducted for each combination of Operating Model and Management Procedure. Details of management objectives and the performance metrics, including the notation used in the plots below can be found in [this table (scroll to page 2)](https://github.com/gavinfay/fluke-mafmc-recdisc/blob/main/docs/Management-Procedures-and-Metric-Descriptions.pdf).   -->


<!-- #### Read in the results objects -->
<!-- These were created with the `performance-metrics.R` script. -->

```{r}
# #metrics <- readRDS("all_results_distrib.rds")
# #median_metrics <- readRDS("all_results_medians.rds")
metrics <- readRDS("sims/metrics.rds")
median_metrics <- readRDS("sims/median_metrics.rds")
state_metrics <- readRDS("sims/full_state_metrics.rds") %>%
  mutate(state = fct_relevel(state,
                             c("MA","RI","CT","NY","NJ","DE","MD","VA","NC")))

# base results with GLM calibration
metrics <- readRDS("sims/metrics_2024-07-07.rds")
median_metrics <- readRDS("sims/median_metrics_2024-07-07.rds")
state_metrics <- readRDS("sims/full_state_metrics_2024-07-07.rds") %>%
  mutate(state = fct_relevel(state,
                             c("MA","RI","CT","NY","NJ","DE","MD","VA","NC")))

# 2BMSY results with GLM calibration
metrics <- readRDS("sims/metrics_2BMSY_2024-07-08.rds")
median_metrics <- readRDS("sims/median_metrics_2BMSY_2024-07-08.rds")
state_metrics <- readRDS("sims/full_state_metrics_2BMSY_2024-07-08.rds") %>%
  mutate(state = fct_relevel(state,
                             c("MA","RI","CT","NY","NJ","DE","MD","VA","NC")))



#metrics
#median_metrics
# state_metrics <- state_metrics %>% 
  #  mutate(state = fct_relevel(state,
   #                          c("MA","RI","CT","NY","NJ","DE","MD","VA","NC")))
```

```{r}
# add radar plot
do_small_radar_plot <- function(metrics) {
  # metrics is a dataframe of metrics, expecting columns
  # metrics <- tibble(metric = rep(letters[1:5],each=3),
  #                   value = runif(15),
  #                   mp = as.character(rep(1:3,5)))
  # # metric 
  # # value
  # # mp (management procedure)
  summaries <- metrics %>% 
    group_by(metric) %>% 
    summarize(min = min(value, na.rm = TRUE),
              max = max(value, na.rm = TRUE)) %>% 
    #pivot_longer(cols = c(2:3),names_to = "mp",
    #             values_to = "value") %>% 
    #pivot_wider(names_from = metric, values_from = value) %>% 
    #arrange(desc(mp)) %>% 
    I()
  #summaries  
  nmetrics <- length(unique(metrics$metric))
  nmp <- length(unique(metrics$mp))
  
  d <- metrics %>% 
    group_by(mp) %>% 
    left_join(summaries) %>% 
    mutate(value = value/(max + 1e-08)) %>% 
    select(mp, metric, value) %>% 
    pivot_wider(names_from = metric, values_from = value) %>% 
    ungroup()
  
  bounds <- tibble(mp = c("max","min"),
                   #"spawning biomass" = c(1,0),
                   #"total catch" = c(1,0),
                   "kept:released" = c(1,0),
                   "kept per trip" = c(1,0),
                   "not overfishing" = c(1,0),
                   "not overfished" = c(1,0),
                   "change_cs" = c(1,0),
                   #"mulen_keep" = c(1,0),
                   #"mulen_release" = c(1,0),
                   #"trophy" = c(1,0),
                   #"rec_removals" = c(1,0),
                   "keep_one" = c(1,0)) #,
                   #"prop_female" = c(1,0),
                   #"ntrips" = c(1,0)) #,
  #filter(metric %in% c("change_cs", "kept per trip", "kept:released", "not overfished", "not overfishing")) %>% 
  #d = c(1,0),
  #e = c(1,0))
  
  dd <- bounds %>% 
    bind_rows(d)
  
  #NEW PLOT
  #colorblind colors
  colors_fill2<-c(alpha("#000000",0.1),
                  alpha("#E69F00",0.1),
                  alpha("#56B4E9",0.1),
                  alpha("#009E73",0.1),
                  alpha("#F0E442",0.1),
                  alpha("#E69F00",0.1),
                  alpha("#56B4E9",0.1),
                  alpha("#009E73",0.1))
  colors_line2<-c(alpha("#000000",0.9),
                  alpha("#E69F00",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#009E73",0.9),
                  alpha("#F0E442",0.9),
                  alpha("#E69F00",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#009E73",0.9))
  colors_line2<-c(alpha("#1b9e77",0.9),
                  alpha("#d95f02",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#dc14cf",0.9),
                  #alpha("#009E73",0.9),
                  alpha("#F0E442",0.9),
                  alpha("#E69F00",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#009E73",0.9))
  
  colors_fill2<-c(alpha("#1b9e77",0.1),
                  alpha("#d95f02",0.1),
                  alpha("#7570b3",0.1),
                  alpha("#e7298a",0.1),
                  alpha("#66a61e",0.1),
                  alpha("#e6ab02",0.1),
                  alpha("#a6761d",0.1),
                  alpha("#d95f02",0.1))
  
  colors_line2<-c(alpha("#1b9e77",0.9),
                  alpha("#d95f02",0.9),
                  alpha("#7570b3",0.9),
                  alpha("#e7298a",0.9),
                  alpha("#66a61e",0.9),
                  alpha("#e6ab02",0.9),
                  alpha("#a6761d",0.9),
                  alpha("#d95f02",0.9))
  
  #colorblind
  radarchart(dd[,-1],seg=5,pcol=colors_line2,
             pfcol=colors_fill2,plwd=2,
             vlabels=names(dd)[-1], vlcex=0.8,
             plty=c(rep(1,7),rep(2,7)),
             pdensity=0)
  rows<<-rownames(dd[-c(1,2),])
  colors_line<<-colors_line2
  legend("bottomright",inset=0,title ="",title.adj = 0.2,
         legend=unique(d$mp),
         pch=16,
         col=colors_line2[1:nmp],
         lty=1, cex=0.8, bty= 'n', y.intersp=1)
  
}

```


```{r}
# nu_state <- state_metrics %>% 
#   group_by(om, mp, metric, isim) %>% 
#   summarize(value = diff(range(value)),
#             .groups = "drop") %>% 
#   filter(metric %in% c("keep_one","kept:released")) %>% 
#   mutate(metric = case_when(
#     metric == "keep_one" ~ "keep_one_range",
#     metric == "kept:released" ~ "kept:rel_range",
#     TRUE ~ metric
#   )) %>% 
#   I()
# #nu_state
# 
# metrics <- metrics %>% 
#   bind_rows(nu_state)
# 
# nu_state_medians <- nu_state %>% 
#   group_by(om, mp, metric) %>% 
#   summarize(value = median(value, na.rm=TRUE)) %>% 
#   filter(metric %in% c("keep_one_range","kept:rel_range")) %>% 
#   I()

state_medians <- state_metrics %>% 
  group_by(om, mp, state, metric) %>% 
  summarize(value = median(value, na.rm=TRUE)) %>% 
  I()


```


<!-- - calculate the relative metrics comparing medians -->

<!-- ```{r} -->
<!-- median_metrics <- median_metrics %>%  -->
<!--   ungroup() %>%  -->
<!--   #select(-isim) %>%  -->
<!--   bind_rows(nu_state_medians) %>%  -->
<!--   I() -->

<!-- mp1_medians <- median_metrics %>%  -->
<!--   ungroup() %>%  -->
<!--   filter(mp == "MP 1") %>%  -->
<!--   select(-mp) %>%  -->
<!--   rename("mp1_val" = value) %>%  -->
<!--   I() -->
<!-- #mp1_medians -->

<!-- nu_medians <- median_metrics %>%  -->
<!--   ungroup() %>%  -->
<!--   left_join(mp1_medians) %>%  -->
<!--   mutate(rel_value = value/mp1_val) %>%  -->
<!--   I() -->
<!-- ``` -->
<!-- <!-- - calculate the relative metrics  --> -->

<!-- ```{r} -->
<!-- mp1_metrics <- metrics %>%  -->
<!--   ungroup() %>%  -->
<!--   filter(mp == "MP 1") %>%  -->
<!--   select(-mp) %>%  -->
<!--   rename("mp1_val" = value) %>%  -->
<!--   I() -->

<!-- nu_metrics <- metrics %>%  -->
<!--   ungroup() %>%  -->
<!--   left_join(mp1_metrics) %>%  -->
<!--   mutate(rel_value = value/mp1_val) %>%  -->
<!--   I() -->
<!-- ``` -->

<!-- <!-- - proportion outperforming mp1 --> -->


<!-- <!-- - create table of all final summary metrics --> -->

<!-- ```{r} -->
<!-- summary_metrics <- nu_medians %>%  -->
<!--   select(om, mp, metric, value) %>%  -->
<!--   filter(metric %in% c("keep_one", -->
<!--                        "cs_per_trip", -->
<!--                        "trophy", -->
<!--                        "not overfished", -->
<!--                        "not overfishing", -->
<!--                        "prop_female", -->
<!--                        "change_cs" -->
<!--                        )) %>%  -->
<!--   I() -->

<!-- summary_rel_metrics <- nu_medians %>%  -->
<!--   select(om, mp, metric, rel_value) %>%  -->
<!--   filter(metric %in% c("kept per trip", -->
<!--                        "keep_one", -->
<!--                        "keep_one_range", -->
<!--                        "kept:released", -->
<!--                        "kept:rel_range", -->
<!--                        "spawning biomass", -->
<!--                        "rel per trip", -->
<!--                        "rec_removals", -->
<!--                        "ntrips" -->
<!--                        #sales/income/GDP compared to mp1 -->
<!--                        )) %>%  -->
<!--   mutate(metric = case_when( -->
<!--     metric == "kept per trip" ~ "kept_per_trip_mp1", -->
<!--     metric == "rel per trip" ~ "rel_per_trip_mp1", -->
<!--     metric == "keep_one" ~ "keep_one_mp1", -->
<!--     metric == "kept:released" ~ "kept:rel_mp1", -->
<!--     metric == "spawning biomass" ~ "ssb_mp1", -->
<!--     metric == "rec_removals" ~ "rec_removals_mp1", -->
<!--     metric == "ntrips" ~ "ntrips_mp1", -->
<!--     metric == "keep_one_range" ~ "keep_one_range_mp1", -->
<!--     metric == "kept:rel_range" ~ "kept:rel_range_mp1", -->
<!--     TRUE ~ metric)) %>%  -->
<!--   rename(value = rel_value) %>%  -->
<!--   I() -->

<!-- summary_metrics <- summary_metrics %>% -->
<!--   bind_rows(summary_rel_metrics) %>%  -->
<!--   filter(metric!="kept:rel_range_mp1") %>%  -->
<!--   I() -->
<!-- #summary_metrics -->

<!-- ``` -->

<!-- <!-- - create table of all final metrics --> -->

<!-- ```{r} -->
<!-- metrics <- nu_metrics %>%  -->
<!--   select(om, mp, metric, isim, value) %>%  -->
<!--   filter(metric %in% c("keep_one", -->
<!--                        "cs_per_trip", -->
<!--                        "trophy", -->
<!--                        "not overfished", -->
<!--                        "not overfishing", -->
<!--                        "prop_female", -->
<!--                        "change_cs" -->
<!--                        )) %>%  -->
<!--   I() -->

<!-- rel_metrics <- nu_metrics %>%  -->
<!--   select(om, mp, metric, isim, rel_value) %>%  -->
<!--   filter(metric %in% c("kept per trip", -->
<!--                        "keep_one", -->
<!--                        "keep_one_range", -->
<!--                        "kept:released", -->
<!--                        "kept:rel_range", -->
<!--                        "spawning biomass", -->
<!--                        "rel per trip", -->
<!--                        "rec_removals", -->
<!--                        "ntrips" -->
<!--                        #sales/income/GDP compared to mp1 -->
<!--                        )) %>%  -->
<!--   mutate(metric = case_when( -->
<!--     metric == "kept per trip" ~ "kept_per_trip_mp1", -->
<!--     metric == "rel per trip" ~ "rel_per_trip_mp1", -->
<!--     metric == "keep_one" ~ "keep_one_mp1", -->
<!--     metric == "kept:released" ~ "kept:rel_mp1", -->
<!--     metric == "spawning biomass" ~ "ssb_mp1", -->
<!--     metric == "rec_removals" ~ "rec_removals_mp1", -->
<!--     metric == "ntrips" ~ "ntrips_mp1", -->
<!--     metric == "keep_one_range" ~ "keep_one_range_mp1", -->
<!--     metric == "kept:rel_range" ~ "kept:rel_range_mp1", -->
<!--     TRUE ~ metric)) %>%  -->
<!--   rename(value = rel_value) %>%  -->
<!--   I() -->

<!-- metrics <- metrics %>% -->
<!--   bind_rows(rel_metrics) %>%  -->
<!--   filter(metric!="kept:rel_range_mp1") %>%  -->
<!--   I() -->
<!-- #summary_metrics -->

<!-- ``` -->

<!-- <!-- ### Metrics by OM & MP --> -->

<!-- <!-- ```{r} --> -->
<!-- <!-- summary <- summary_metrics %>%  --> -->
<!-- <!--   mutate(om = factor(om), --> -->
<!-- <!--          om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3")) %>%  --> -->
<!-- <!--   group_by(mp, metric) %>%  --> -->
<!-- <!--   mutate(val2 = value/max(value, na.rm=TRUE)) %>%  --> -->
<!-- <!--   # filter(!metric %in% c("total catch", "expense", "cs_per_trip", --> -->
<!-- <!--   #                       "mulen_keep", --> -->
<!-- <!--   #                       "mulen_release", --> -->
<!-- <!--   #                       "not overfished", --> -->
<!-- <!--   #                       "prop_female")) %>%  --> -->
<!-- <!--   ggplot() + --> -->
<!-- <!--   aes(x = metric, y = val2, col = om, group = mp) + --> -->
<!-- <!--   geom_point() + --> -->
<!-- <!--   coord_flip() + --> -->
<!-- <!--   facet_grid(~mp) + --> -->
<!-- <!--   geom_hline(yintercept = 0, lty=2, alpha =0.5) + --> -->
<!-- <!--   theme(legend.position = "bottom") + --> -->
<!-- <!--         #axis.text.y = element_blank()) + --> -->
<!-- <!--   guides(fill = guide_legend(nrow = 1)) --> -->
<!-- <!-- summary --> -->

<!-- <!-- ``` --> -->


<!-- ### Performance metrics across management alternatives for all operating model scenarios -->
<!-- ```{r} -->
<!-- p2 <- summary_metrics %>%  -->
<!--   mutate(om = factor(om), -->
<!--          om = fct_recode(om, "Base" = "1","MRIP Bias" = "2","Shift" = "3"), -->
<!--          mp2 = fct_recode(mp, -->
<!--                           "status quo" = "MP 1", -->
<!--                           "minsize-1" = "MP 2",  -->
<!--                           "season" = "MP 3",  -->
<!--                           "region" = "MP 4", -->
<!--                           #"c1@14" = "MP 5",  -->
<!--                           "3@17" = "MP 6", -->
<!--                           "1@16-19" = "MP 7", -->
<!--                           "slot" = "MP 8"), -->
<!--          metric = factor(metric, levels = c("keep_one", -->
<!--                                             "kept_per_trip_mp1", -->
<!--                                             "cs_per_trip", -->
<!--                                             "trophy", -->
<!--                                             "keep_one_mp1", -->
<!--                                             "keep_one_range_mp1", -->
<!--                                             "kept:rel_mp1", -->
<!--                                             #"kept:rel_range_mp1", -->
<!--                                             "not overfished", -->
<!--                                             "not overfishing", -->
<!--                                             "ssb_mp1", -->
<!--                                             "rel_per_trip_mp1", -->
<!--                                             "rec_removals_mp1", -->
<!--                                             "prop_female", -->
<!--                                             "ntrips_mp1", -->
<!--                                             "change_cs"#, -->
<!--                                             #"gdp_mp1" -->
<!--                                             ))) %>%  -->
<!--   #filter(om == 1) %>%  -->
<!--   ggplot() + -->
<!--   aes(x = mp2, y = value, col = mp2, shape = om) + -->
<!--   #geom_boxplot(outlier.shape=NA) + -->
<!--   geom_point() + -->
<!--   geom_line(aes(x = mp2, y = value, group = om), col = "gray") + -->
<!--   geom_point() +  -->
<!--   scale_color_brewer(type = "qual", palette = 2) + -->
<!--   facet_wrap(~metric, scale = "free_y", drop = F) + -->
<!--   ylab("") + -->
<!--   xlab("") + -->
<!--   theme_bw() + -->
<!--   theme(legend.position = "bottom", -->
<!--         axis.text.x = element_blank()) + -->
<!--   labs(fill = "", -->
<!--        col = "") + -->
<!--   guides(col = guide_legend(nrow = 2), -->
<!--          shape = guide_legend(nrow = 2)) -->
<!-- ggsave("outputs/plots/median-metrics-alloms-slides.png",p2,width=9,height=5) -->
<!-- p2 -->
<!-- ``` -->

<!-- ### Base Operating Model Scenario -->


<!-- ```{r} -->
<!-- metrics2 <- metrics %>%  -->
<!--   mutate(om = factor(om), -->
<!--          om = fct_recode(om, "Base" = "1","MRIP Bias" = "2","Shift" = "3"), -->
<!--          mp2 = fct_recode(mp, -->
<!--                           "status quo" = "MP 1", -->
<!--                           "minsize-1" = "MP 2",  -->
<!--                           "season" = "MP 3",  -->
<!--                           "region" = "MP 4", -->
<!--                           #"c1@14" = "MP 5",  -->
<!--                           "3@17" = "MP 6", -->
<!--                           "1@16-19" = "MP 7", -->
<!--                           "slot" = "MP 8"), -->
<!--          metric = factor(metric, levels = c("keep_one", -->
<!--                                             "kept_per_trip_mp1", -->
<!--                                             "cs_per_trip", -->
<!--                                             "trophy", -->
<!--                                             "keep_one_mp1", -->
<!--                                             "keep_one_range_mp1", -->
<!--                                             "kept:rel_mp1", -->
<!--                                             "kept:rel_range_mp1", -->
<!--                                             "not overfished", -->
<!--                                             "not overfishing", -->
<!--                                             "ssb_mp1", -->
<!--                                             "rel_per_trip_mp1", -->
<!--                                             "rec_removals_mp1", -->
<!--                                             "prop_female", -->
<!--                                             "ntrips_mp1", -->
<!--                                             "change_cs"#, -->
<!--                                             #"gdp_mp1" -->
<!--                                             )))  -->

<!-- ``` -->
```{r}
scen_lookup <- read_sheet("https://docs.google.com/spreadsheets/d/17PZz1vlJDw8lMd0aewDkYD_zWsAfLMQWPUb--1imqGk/edit?gid=0#gid=0") %>% 
  janitor::clean_names() %>% 
  rename(mp = run_number)
scen_lookup
```


```{r}
metrics2 <- metrics %>% 
  left_join(scen_lookup) %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "Base" = "1","MRIP Bias" = "2","Shift" = "3"),
         mp2 = fct_recode(factor(hcr),
                          "rhl" = "11",
                          "perc_change" = "6", 
                          "refpt" = "8",
                          "bmatrix" = "10"),
         mp3 = fct_collapse(factor(reg_to_change),
                          "bag" = "1",
                          "season" = "3",
                          "minlen" = "2"),
         mp3 = fct_relevel(mp3, "bag", "season"),
         #value = ifelse(metric == "exp_keep", 0.39*value, value),
         metric = factor(metric, levels = c("keep_one",
                                            "kept per trip", #_mp1",
                                            "cs_per_trip",
                                            "trophy",
                                            #"keep_one_mp1",
                                            "keep_one_range", #_mp1",
                                            "kept:released", #_mp1",
                                            #"kept:rel_range", #_mp1",
                                            "not overfished",
                                            "not overfishing",
                                            "spawning biomass", #_mp1",
                                            "rel per trip", #_mp1",
                                            "rec_removals", #_mp1",
                                            "prop_female",
                                            "ntrips", #_mp1",
                                            "change_cs"#,
                                            #"exp_keep"
                                            #"gdp_mp1"
                                            ))) 

```


```{r}
# add boxplots
p2 <- metrics2 %>% 
  drop_na() %>% 
  filter(!(metric %in% c("change_cs","keep_one_range"))) %>% 
  droplevels() %>% 
  #filter(om == "Base") %>% 
  ggplot() +
  aes(x = mp3, y = value, fill = mp2) +
  #aes(x = mp2, y = value, fill = mp3) +
  geom_boxplot(outlier.shape=NA) +
  scale_fill_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, scale = "free_y", drop = F) +
  ylab("performance metric value") +
  xlab("regulation to change") +
  theme_bw() +
  theme(legend.position = "bottom") + #,
        #axis.text.x = element_blank()) +
  labs(fill = "HCR") + #,
       #subtitle = "Base scenario") +
  guides(fill = guide_legend(nrow = 1))
# add table summaries
#ggsave("boxplot-metrics.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om2.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om3.png",p2,width=8,height=8)
#ggsave("boxplot-metrics.png",p2,width=9,height=6)
#ggsave("boxplot-metrics_estF.png",p2,width=9,height=6)
p2
```

<!-- #### Tradeoffs among key metrics for the Base operating model scenario -->
<!-- ```{r} -->
<!-- # radar chart - not sure how to save this to file automagically -->
<!-- p3 <- median_metrics %>%  -->
<!--   mutate(om = factor(om), -->
<!--          om = fct_recode(om, "Base" = "1","MRIP Bias" = "2","Shift" = "3")) %>%  -->
<!--   filter(om == "Base") %>%  -->
<!--   mutate(mp = fct_recode(mp, -->
<!--                    "status quo" = "MP 1", -->
<!--                    "minsize-1" = "MP 2",  -->
<!--                    "season" = "MP 3",  -->
<!--                    "region" = "MP 4", -->
<!--                    #"c1@14" = "MP 5",  -->
<!--                    "3@17" = "MP 6", -->
<!--                    "1@16-19" = "MP 7", -->
<!--                    "slot" = "MP 8")) %>%  -->
<!--   #filter(!metric %in% c("change_cs", "cs_per_trip")) %>%  -->
<!--   #filter(!metric %in% c("expense","cs_per_trip","total catch")) %>%  -->
<!--   filter(metric %in% c("change_cs", "kept per trip", "kept:released", "not overfished", "not overfishing", "keep_one")) %>%  -->
<!--   do_small_radar_plot() -->

<!-- ``` -->


### State level metrics

20264-06-17 GF: not computed anything below here for the 2024 runs

```{r}
do_state_bp <- function(state_metrics = NULL) {
  title_metric <- state_metrics$metric[1]
  state_bp <- state_metrics %>% 
    #filter(metric %in% c("change_cs")) %>%  #c("kept per trip")) %>% 
  ggplot() +
  aes(x = mp, y = value, fill = mp) +
  geom_boxplot(outlier.shape=NA) +
  scale_fill_brewer(type = "qual", palette = 2) +
  facet_wrap(~state, scale = "free_y") +
  #facet_wrap(~metric, scale = "free_y") +
  ylab("") +
  xlab("") +
  theme_bw() +
  #ylim(0,5e+06) +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "",
       title = title_metric) + #kept per trip") +
  guides(fill = guide_legend(nrow = 1))
  return(state_bp)
}

```


<!-- #### State-by-state metrics for the Base Operating Model scenario -->
```{r}
state_bp <- state_metrics %>% 
  filter(om == 1) %>% 
   mutate(mp = fct_recode(mp,
                   "status quo" = "MP 1",
                   "minsize-1" = "MP 2", 
                   "season" = "MP 3", 
                   "region" = "MP 4",
                   #"c1@14" = "MP 5", 
                   "3@17" = "MP 6",
                   "1@16-19" = "MP 7",
                   "slot" = "MP 8")) %>% 
  nest_by(metric,.keep = TRUE) %>% 
  mutate(bp = list(do_state_bp(data)))
```

### State-by-state metrics for the Base Operating Model scenario {.tabset}
```{r, results = 'asis', echo = FALSE}
for (i in seq_along(state_bp$metric)){
  tmp <- state_bp$bp[[i]]
  cat("####", tmp$data$metric[1], " \n")
  print(tmp)
  cat(" \n\n")
  }
```

###

```{r}
state_bp <- state_metrics %>% 
  filter(om == 2) %>% 
   mutate(mp = fct_recode(mp,
                   "status quo" = "MP 1",
                   "minsize-1" = "MP 2", 
                   "season" = "MP 3", 
                   "region" = "MP 4",
                   #"c1@14" = "MP 5", 
                   "3@17" = "MP 6",
                   "1@16-19" = "MP 7",
                   "slot" = "MP 8")) %>%   
  nest_by(metric,.keep = TRUE) %>% 
  mutate(bp = list(do_state_bp(data)))
```

### State-by-state metrics for the MRIP Bias Operating Model scenario {.tabset}
```{r, results = 'asis', echo = FALSE}
for (i in seq_along(state_bp$metric)){
  tmp <- state_bp$bp[[i]]
  cat("####", tmp$data$metric[1], " \n")
  print(tmp)
  cat(" \n\n")
  }
```

###

```{r}
state_bp <- state_metrics %>% 
  filter(om == 3) %>% 
   mutate(mp = fct_recode(mp,
                   "status quo" = "MP 1",
                   "minsize-1" = "MP 2", 
                   "season" = "MP 3", 
                   "region" = "MP 4",
                   #"c1@14" = "MP 5", 
                   "3@17" = "MP 6",
                   "1@16-19" = "MP 7",
                   "slot" = "MP 8")) %>%   
  nest_by(metric,.keep = TRUE) %>% 
  mutate(bp = list(do_state_bp(data)))
```

### State-by-state metrics for the Distribution Shift Operating Model scenario {.tabset}
```{r, results = 'asis', echo = FALSE}
for (i in seq_along(state_bp$metric)){
  tmp <- state_bp$bp[[i]]
  cat("####", tmp$data$metric[1], " \n")
  print(tmp)
  cat(" \n\n")
  }
```

###

### How many states do better than the status quo management alternative?
```{r}
state_medians <- state_metrics %>% 
  group_by(om, mp, metric, state) %>% 
  summarize(value = median(value, na.rm=TRUE)) %>% 
  ungroup()

mp1 <- state_medians %>% 
  filter(mp == "MP 1") %>% 
  mutate(mp1_val = value) %>% 
  select(metric, mp1_val, om, state)
  
beat_mp1 <- state_medians %>% 
  #filter(mp != "MP 1") %>% 
  left_join(mp1) %>% 
  mutate(beat_mp1 = ifelse(value > mp1_val, 1,0)) %>% 
  group_by(om, mp, metric) %>% 
  summarize(nbeat = sum(beat_mp1, na.rm=TRUE))
#beat_mp1

```

```{r}
nbeat_plot <- beat_mp1 %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "Base" = "1","MRIP Bias" = "2","Shift" = "3"),
         mp = fct_expand(mp,"MP 1"),
         mp = fct_relevel(mp, "MP 1")) %>% 
  ggplot() +
  aes(x = mp, y = nbeat, col = mp, shape = om) +
  #geom_boxplot(outlier.shape=NA) +
  geom_point() +
  geom_line(aes(x = mp, y = nbeat, group = om), col = "gray") +
  scale_color_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, drop = F) +
  ylab("") +
  xlab("") +
  ylim(0,10) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "") +
  guides(col = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
nbeat_plot
ggsave("outputs/plots/nstates_beat_mp1.png",nbeat_plot,width=9,height=5)
```


<!-- ```{r} -->
<!-- mp1 <- state_metrics %>%  -->
<!--   filter(mp == "MP 1") %>%  -->
<!--   mutate(mp1_val = value) %>%  -->
<!--   select(metric, mp1_val, om, isim, state) -->

<!-- beat_mp1 <- state_metrics %>%  -->
<!--   filter(mp != "MP 1") %>%  -->
<!--   left_join(mp1) %>%  -->
<!--   mutate(beat_mp1 = ifelse(value > mp1_val, 1,0)) %>%  -->
<!--   group_by(om, mp, metric, state) %>%  -->
<!--   summarize(prop = mean(beat_mp1, na.rm=TRUE)) -->

<!-- beat_mp1 -->


<!-- ``` -->

