---
title: "performance-metric-kw"
author: "Kamran Walsh"
date: "2024-08-06"
output: html_document
---

Functions:
```{r}
#projection plot
projection.plot <- function(project.results) {
  project.results <- project.results %>% 
    #filter(type %in% c("biomass","catch")) %>%
    I()
  project.results %>% 
    #group_by(scenario, type, year) %>% 
    #median_qi(value, .width = c(.5, .8, .95)) %>%
    ggplot() +  
    stat_lineribbon(aes(x = year, y = value, fill = scenario),
                    #show.legend = FALSE,
                    alpha = 0.35) +
    # geom_lineribbon(aes(x = year, y = value, ymin = .lower, ymax = .upper, fill = scenario),
    #                 show.legend = FALSE) +
    scale_fill_brewer(type = "qual", palette = 2) +
    facet_wrap(~type, scale = "free") + 
    geom_line(aes(y=value,x=year,group=scenario),data = subset(project.results, type != "index" & isim==1), lty=1,lwd=0.5,col=gray(0.7),alpha=0.5) +
    geom_line(aes(y=value,x=year,group=scenario),data = subset(project.results, type != "index" & isim==2), lty=1,lwd=0.5,col=gray(0.7),alpha=0.5) +
    geom_line(aes(y=value,x=year,group=scenario),data = subset(project.results, type != "index" & isim==3), lty=1,lwd=0.5,col=gray(0.7),alpha=0.5) +
    geom_line(aes(y=value,x=year,group=scenario),data = subset(project.results, type != "index" & isim==4), lty=1,lwd=0.5,col=gray(0.7),alpha=0.5) +
    ylim(0,NA) + 
    ylab("") + 
    theme_bw() +
    theme(legend.position="bottom") + #,
          #axis.text.y = element_blank()) +
    labs(fill = "")
}

library(tidyverse)
library(ggdist)
library(scales)
library(fmsb)
read_results <- function(scendir =  "~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/"
                         ,scen.name="compare",
                         om.name = 1,
                         fsim = 1) {
  
 # scendir <- "~/Dropbox/fluke-mse/sims/2022-07-25/01-01/"
  #scendir = "~/research/mafmc-recmeasures/sims/001/"
  #scen.name="MP 1"
  #om.name = 1
  #fsim = 1
  print(scendir)

spawbio <- read.table(paste0(scendir,"spawbio.out"), header = TRUE)
totcatch <- read.table(paste0(scendir, "totcatch.out"), header = TRUE)
if(om.name!=1) sexcatch <- read.table(paste0(scendir, "sexcatch.out"), header = TRUE)
recoutput <- read.table(paste0(scendir, "recoutput.out"), header = FALSE, skip = 1) #TRUE)
recoutput2 <- read.table(paste0(scendir, "recoutput2.out"), header = FALSE, skip = 1) #TRUE)
rbctrack <- read.table(paste0(scendir, "rbctrack.out"), header = FALSE, skip = 1)
fout <- read.table(paste0(scendir,"frate.out"), header = TRUE)
names(spawbio) <- str_sub(names(spawbio), start=2)
names(totcatch) <- str_sub(names(totcatch), start=2)
if(om.name!=1) names(sexcatch) <- str_sub(names(sexcatch), start=2)
names(fout) <- str_sub(names(fout), start=2)
nsim = length(unique(rbctrack[,1]))
results <- spawbio %>% 
  as_tibble() %>% 
  rowid_to_column(var = "isim") %>% 
  pivot_longer(cols= 2:ncol(.), names_to = "year", values_to = "biomass") %>% 
  mutate(year = as.integer(year)) %>% 
  I()
res2 <- totcatch %>% 
  tibble() %>% 
  #rowid_to_column(var = "isim") %>% 
  mutate(isim = rep(1:(nrow(.)/4),each=4)) %>% 
  rename(fleet = L) %>%
  select(isim,everything()) %>% 
  pivot_longer(cols= 3:ncol(.), names_to = "year", values_to = "catch") %>% 
  mutate(year = as.integer(year)) %>% 
  group_by(isim, year) %>% 
  summarize(totcat_wt = sum(catch),
             keep_wt = sum(catch*(fleet==3)),
             release_wt = sum(catch*(fleet==4))) %>% 
  #pivot_wider(names_from = fleet, names_glue = "fleet_{fleet}", values_from = catch) %>% 
  I()
#res2
results <- results %>% 
  left_join(res2)

#recoutput - getting rid of extra outpt from iscen=1 & unfinished simulations
nyrs <- length(unique(recoutput[,2]))
# dummy <- recoutput %>% 
#   tibble() %>% 
#   slice(1:nyrs)
# dummy2 <- recoutput %>% 
#   tibble() %>% 
#   slice(((nyrs+1):nrow(.))) %>% 
#   filter(V1 != 1)
# temp <- bind_rows(dummy,dummy2)
# nsim <- floor(nrow(temp)/nyrs)
# recoutput <-  temp %>% 
#   slice((1:(nsim*nyrs)))

recoutput[,1] <- rep(1:nsim, each = 2*nyrs)
res3 <- recoutput[,1:4] %>% as_tibble()
names(res3) <- c("isim", "year", "type", "number") #,"trips")
res3 <- res3 %>% 
  mutate(#year = 2019 + year,
    type = ifelse(type==1, "keep_num", "release_num")) %>% 
  pivot_wider(names_from = "type", values_from = "number") %>% 
  I()


#recoutput2 - getting rid of extra outpt from iscen=1 & unfinished simulations
nyrs <- length(unique(recoutput2[,2]))
# dummy <- recoutput2 %>% 
#   tibble() %>% 
#   slice(1:(10*nyrs))
# dummy2 <- recoutput2 %>% 
#   tibble() %>% 
#   slice(((10*nyrs+1):nrow(.))) %>% 
#   filter(V1 != 1)
# temp <- bind_rows(dummy,dummy2)
# nsim <- floor(nrow(temp)/nyrs)
# recoutput2 <-  temp %>% 
#   slice((1:(nsim*nyrs*10)))
recoutput2[,1] <- rep(1:nsim, each = 10*nyrs)
names(recoutput2) <- c("isim","year","state","n_keep","n_release","ntrips","nchoice","change_cs","cost",
                        "keep_one", "mulen_keep","mulen_release","trophy")
#names(recoutput2) <- c("isim","year","state","ntrips","nchoice","change_cs","cost",
#                       "keep_one", "mulen_keep","mulen_release","trophy")
coast_recoutput <- recoutput2 %>% 
  filter(state == 1)

res3 <- recoutput[,1:4] %>% as_tibble()
names(res3) <- c("isim", "year", "type", "number") #,"trips")
res3 <- res3 %>% 
  mutate(#year = 2019 + year,
    type = ifelse(type==1, "keep_num", "release_num")) %>% 
  pivot_wider(names_from = "type", values_from = "number") %>% 
  left_join(coast_recoutput) %>% 
  I()

results <- results %>% 
  left_join(res3)

rbc2 <- rbctrack %>% 
  tibble() %>% 
  select(1,2,4,15,9,10,11,12,18,22) %>% 
  I()
rbc2 <- rbctrack %>% 
  tibble() %>% 
  select(1,2,4,8,9,11,12,18,15:17) %>% 
  I()
#names(rbc2) <- c("isim","year","abc","fmsy","est_ofl","true_ofl","rhl","bmsy","msy","fem_ssb")
names(rbc2) <- c("isim","year","abc","fmsy","est_ofl","rhl","bmsy","exp_keep","seaslen","bag","minlen") #,"msy")
rbc2 <- rbc2 %>% 
  mutate(exp_keep = as.numeric(ifelse(exp_keep == "******************",NA,exp_keep))) %>% 
  mutate(year = 2019 + 2*year - 1) %>% 
  I()
results <- results %>% 
  left_join(rbc2)
  #mutate(scenario = rep("coastwide 14",nrow(.)))

# temp <- results %>% 
#   filter(year!=2019) %>% 
#   fill("abc","fmsy","est_ofl","true_ofl","rhl","bmsy","msy","fem_ssb")

temp <- results %>% 
  filter(year!=2019) %>% 
  fill("abc","fmsy","est_ofl",,"rhl","bmsy","exp_keep","seaslen","bag","minlen")

results <- results %>% 
  filter(year==2019) %>% 
  bind_rows(temp) %>% 
  arrange(isim,year)


# refpts <- read.table("mse/coast14/refpts.out", header = FALSE, skip = 1)
# names(refpts) <- c("isim", "fref", "bref", "cref")
# coast_results <- coast_results %>% 
#   left_join(refpts)

# 2024-06-14 GF commenting out because F is coming from rbctrack.out file (currently estF)
res4 <- fout %>%
  as_tibble() %>%
  rowid_to_column(var = "isim") %>%
  pivot_longer(cols= 2:ncol(.), names_to = "year", values_to = "frate") %>%
  mutate(year = as.integer(year)) %>%
  I()
results <- results %>%
  left_join(res4)

if(om.name!=1)  {
res5 <- sexcatch %>%
  tibble() %>%
  #rowid_to_column(var = "isim") %>%
  mutate(isim = rep(1:(nrow(.)/4),each=4)) %>%
  rename(fleet = L) %>%
  select(isim,everything()) %>%
  pivot_longer(cols= 3:ncol(.), names_to = "year", values_to = "prop_female") %>%
  mutate(year = as.integer(year)) %>%
  filter(fleet == 3) %>%
  select(-fleet) %>%
  # group_by(isim, year) %>%
  # summarize(totcat_wt = sum(catch),
  #           prop_fem = sum(catch*(fleet==3)),
  #           release_wt = sum(catch*(fleet==4))) %>%
  #pivot_wider(names_from = fleet, names_glue = "fleet_{fleet}", values_from = catch) %>%
  I()
#res5
results <- results %>%
  left_join(res5)
}

results <- results %>% 
  mutate(scenario = rep(scen.name,nrow(.)),
         om = rep(om.name, nrow(.)),
         isim = isim + fsim -1)

return(results)
}

get_diag_ts <- function(results) {
  
diag_ts <- results %>% 
  mutate(keep_to_rel = keep_num/release_num,
         change_cs = change_cs*-1,
         "kept per trip" = 1000*keep_num/ntrips,
         "rel per trip" = 1000*release_num/ntrips,
         "F/Fref" = frate/fmsy,
         "B/Bref" = biomass/bmsy,
         "expense" = cost,
         cs_per_trip = change_cs/ntrips,
         rec_removals = keep_wt + release_wt,
         keep_one = keep_one/ntrips,
         keep_to_exp = 1000*keep_num / (0.39*exp_keep))  %>% 
  select(om, scenario, isim, year, biomass, totcat_wt, rec_removals, keep_to_rel, "kept per trip", "rel per trip",
         "F/Fref", "B/Bref",
         mulen_keep,
         mulen_release,
         trophy,
         expense,
         change_cs,
         ntrips,
         keep_one,
         cs_per_trip,
         prop_female,
         keep_to_exp,
         bag,
         minlen,
         seaslen,
         exp_keep
         ) %>% 
  rename("spawning biomass" = biomass,
         "total catch" = totcat_wt,
         "kept:released" = keep_to_rel) %>% 
  pivot_longer(cols=c("spawning biomass","total catch","kept:released", "kept per trip", 
                      "rel per trip",
                      "F/Fref", "B/Bref",
                      rec_removals,
                      mulen_keep,
                      mulen_release,
                      trophy,
                      expense,
                      change_cs,
                      ntrips,
                      keep_one,
                      cs_per_trip,
                      prop_female,
                      keep_to_exp,
                      bag,
                      minlen,
                      seaslen,
                      exp_keep
                      ),names_to = "type", values_to = "value") %>% 
  I()
 return(diag_ts)
}


get_om1_sexcatch <- function(scendir, scen.name) {
fsim=1
sexcatch <- read.table(paste0(scendir, "sexcatch.out"), header = TRUE)
names(sexcatch) <- str_sub(names(sexcatch), start=2)

  res5 <- sexcatch %>%
    tibble() %>%
    #rowid_to_column(var = "isim") %>%
    mutate(isim = rep(1:(nrow(.)/4),each=4)) %>%
    rename(fleet = L) %>%
    select(isim,everything()) %>%
    pivot_longer(cols= 3:ncol(.), names_to = "year", values_to = "prop_female") %>%
    mutate(year = as.integer(year)) %>%
    filter(fleet == 3) %>%
    select(-fleet) %>%
    # group_by(isim, year) %>%
    # summarize(totcat_wt = sum(catch),
    #           prop_fem = sum(catch*(fleet==3)),
    #           release_wt = sum(catch*(fleet==4))) %>%
    #pivot_wider(names_from = fleet, names_glue = "fleet_{fleet}", values_from = catch) %>%
    I()
  #res5
  
  results <- res5 %>% 
    mutate(scenario = rep(scen.name,nrow(.)),
           om = rep(1, nrow(.)),
           isim = isim + fsim -1)
  return(results)
}

#add small radar plot
do_small_radar_plot <- function(metrics) {
  # metrics is a dataframe of metrics, expecting columns
  # metrics <- tibble(metric = rep(letters[1:5],each=3),
  #                   value = runif(15),
  #                   mp = as.character(rep(1:3,5)))
  # # metric 
  # # value
  # # mp (management procedure)
  summaries <- metrics %>% 
    group_by(metric) %>% 
    summarize(min = min(value, na.rm = TRUE),
              max = max(value, na.rm = TRUE)) %>% 
    #pivot_longer(cols = c(2:3),names_to = "mp",
    #             values_to = "value") %>% 
    #pivot_wider(names_from = metric, values_from = value) %>% 
    #arrange(desc(mp)) %>% 
    I()
  #summaries  
  nmetrics <- length(unique(metrics$metric))
  nmp <- length(unique(metrics$mp))
  
  d <- metrics %>% 
    group_by(mp) %>% 
    left_join(summaries) %>% 
    mutate(value = value/(max + 1e-08)) %>% 
    select(mp, metric, value) %>% 
    pivot_wider(names_from = metric, values_from = value) %>% 
    ungroup()
  
  bounds <- tibble(mp = c("max","min"),
                   #"spawning biomass" = c(1,0),
                   #"total catch" = c(1,0),
                   "kept:released" = c(1,0),
                   "kept per trip" = c(1,0),
                   "not overfishing" = c(1,0),
                   "not overfished" = c(1,0),
                   "change_cs" = c(1,0),
                   #"mulen_keep" = c(1,0),
                   #"mulen_release" = c(1,0),
                   #"trophy" = c(1,0),
                   #"rec_removals" = c(1,0),
                   "keep_one" = c(1,0)) #,
                   #"prop_female" = c(1,0),
                   #"ntrips" = c(1,0)) #,
  #filter(metric %in% c("change_cs", "kept per trip", "kept:released", "not overfished", "not overfishing")) %>% 
  #d = c(1,0),
  #e = c(1,0))
  
  dd <- bounds %>% 
    bind_rows(d)
  
  #NEW PLOT
  #colorblind colors
  colors_fill2<-c(alpha("#000000",0.1),
                  alpha("#E69F00",0.1),
                  alpha("#56B4E9",0.1),
                  alpha("#009E73",0.1),
                  alpha("#F0E442",0.1),
                  alpha("#E69F00",0.1),
                  alpha("#56B4E9",0.1),
                  alpha("#009E73",0.1))
  colors_line2<-c(alpha("#000000",0.9),
                  alpha("#E69F00",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#009E73",0.9),
                  alpha("#F0E442",0.9),
                  alpha("#E69F00",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#009E73",0.9))
  colors_line2<-c(alpha("#1b9e77",0.9),
                  alpha("#d95f02",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#dc14cf",0.9),
                  #alpha("#009E73",0.9),
                  alpha("#F0E442",0.9),
                  alpha("#E69F00",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#009E73",0.9))
  
  colors_fill2<-c(alpha("#1b9e77",0.1),
                  alpha("#d95f02",0.1),
                  alpha("#7570b3",0.1),
                  alpha("#e7298a",0.1),
                  alpha("#66a61e",0.1),
                  alpha("#e6ab02",0.1),
                  alpha("#a6761d",0.1),
                  alpha("#d95f02",0.1))
  
  colors_line2<-c(alpha("#1b9e77",0.9),
                  alpha("#d95f02",0.9),
                  alpha("#7570b3",0.9),
                  alpha("#e7298a",0.9),
                  alpha("#66a61e",0.9),
                  alpha("#e6ab02",0.9),
                  alpha("#a6761d",0.9),
                  alpha("#d95f02",0.9))
  
  #colorblind
  radarchart(dd[,-1],seg=5,pcol=colors_line2,
             pfcol=colors_fill2,plwd=2,
             vlabels=names(dd)[-1], vlcex=0.8,
             plty=c(rep(1,7),rep(2,7)),
             pdensity=0)
  rows<<-rownames(dd[-c(1,2),])
  colors_line<<-colors_line2
  legend("bottomright",inset=0,title ="",title.adj = 0.2,
         legend=unique(d$mp),
         pch=16,
         col=colors_line2[1:nmp],
         lty=1, cex=0.8, bty= 'n', y.intersp=1)
  
}
```

Switch 
```{r}

HCRtoplot <- "SPLIT"
#change the folder names for the scenarios you want to summarize results for and give them a unique name
```

Read in Data:
- use numbers if merging to spreadsheet, character names (e.g. "BTable3.1") if using code in here

BASE2 sinatra_split "BASE2split" 4 reg types parallel
```{r}
params <- if(HCRtoplot == "BASE2split"){list(
  scendir = c( #BBM
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50BBM2/sim1_bag/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50BBM2/sim2_length/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50BBM2/sim3_season/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50BBM2/sim4_all/",
       
            #BRP
            "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50BRP/sim1_bag/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50BRP/sim2_length/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50BRP/sim3_season/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50BRP/sim4_all/",
  
             #PCA 
         "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50PCA/sim1_bag/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50PCA/sim2_length/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50PCA/sim3_season/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50PCA/sim4_all/",
  
               #NCA
          "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50NCA/sim1_bag/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50NCA/sim2_length/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50NCA/sim3_season/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50NCA/sim4_all/"
        ),
  scen.name = c(
1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16
  ),
  fsim = rep(1,16))
}
```

"BTable3", 
"LTable3",  
"STable3", 
"ATable3",  

"BTable3.1",
"LTable3.1", 
"STable3.1", 
"ATable3.1", 

"BTable3.2",
"LTable3.2", 
"STable3.2",
"ATable3.2",

"BTable3.3",
"LTable3.3", 
"STable3.3", 
"ATable3.3"

BASE2 sinatra original "BASE2"
```{r}
params <- if(HCRtoplot == "BASE2"){list( #was 102024 before 11/22/24
  scendir = c( #BBM
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50BBM2/sim1_bag/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50BBM2/sim2_length/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50BBM2/sim3_season/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50BBM2/sim4_all/",
       
            #BRP
            "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50BRP/sim1_bag/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50BRP/sim2_length/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50BRP/sim3_season/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50BRP/sim4_all/",
  
             #PCA 
         "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50PCA/sim1_bag/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50PCA/sim2_length/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50PCA/sim3_season/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102024/50PCA/sim4_all/",
  
               #NCA
          "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50NCA/sim1_bag/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50NCA/sim2_length/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50NCA/sim3_season/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102624/50NCA/sim4_all/"
        ),
  scen.name = c(
"BTable3",
"LTable3",  
"STable3", 
"ATable3",  

"BTable3.1",
"LTable3.1", 
"STable3.1", 
"ATable3.1", 

"BTable3.2",
"LTable3.2", 
"STable3.2",
"ATable3.2",

"BTable3.3",
"LTable3.3", 
"STable3.3", 
"ATable3.3"
  ),
  fsim = rep(1,16))
}
```

BASE3 <- parallel sims sinatra_split "BASE3"  
```{r}
params <- if(HCRtoplot == "BASE3"){list( #check splits 1-80 vs 1,1,1,1,1,2,2,2,2,2, etc. with code 
  scendir = c( #BBM
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/1_bag/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/1_bag/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/1_bag/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/1_bag/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/1_bag/sim41_50/",
    
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/2_length/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/2_length/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/2_length/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/2_length/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/2_length/sim41_50/",
       
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/3_season/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/3_season/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/3_season/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/3_season/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/3_season/sim41_50/",
       
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/4_all/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/4_all/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/4_all/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/4_all/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BBM/4_all/sim41_50/",
       
            #BRP
     "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/1_bag/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/1_bag/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/1_bag/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/1_bag/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/1_bag/sim41_50/",
    
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/2_length/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/2_length/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/2_length/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/2_length/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/2_length/sim41_50/",
       
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/3_season/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/3_season/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/3_season/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/3_season/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/3_season/sim41_50/",
       
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/4_all/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/4_all/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/4_all/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/4_all/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/BRP/4_all/sim41_50/" ,
 
          
             #PCA 
   "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/1_bag/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/1_bag/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/1_bag/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/1_bag/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/1_bag/sim41_50/",
    
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/2_length/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/2_length/sim11_20/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/2_length/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/2_length/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/2_length/sim41_50/",
       
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/3_season/sim1_10/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/3_season/sim11_20/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/3_season/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/3_season/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/3_season/sim41_50/",
       
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/4_all/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/4_all/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/4_all/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/4_all/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/PCA/4_all/sim41_50/",
 
        
               #NCA
      "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/1_bag/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/1_bag/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/1_bag/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/1_bag/sim41_50/",
    
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/2_length/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/2_length/sim11_20/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/2_length/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/2_length/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/2_length/sim41_50/",

    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/3_season/sim1_10/",
                 "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/3_season/sim11_20/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/3_season/sim21_30/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/3_season/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/3_season/sim41_50/",
       
    "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/4_all/sim1_10/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/4_all/sim11_20/",
                "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/4_all/sim21_30/",
             "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/4_all/sim31_40/",
               "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/102124/NCA/4_all/sim41_50/"
            ),
  scen.name = c(
    "BTable3_1",
"BTable3_2", 
"BTable3_3", 
"BTable3_4", 
"BTable3_5",  
"LTable3_1",  
"LTable3_2", 
"LTable3_3", 
"LTable3_4", 
"LTable3_5",
"STable3_1", 
"STable3_2", 
"STable3_3", 
"STable3_4",  
"STable3_5",  
"ATable3_1",  
"ATable3_2", 
"ATable3_3", 
"ATable3_4", 
"ATable3_5",

"BTable3.1_1",
"BTable3.1_2",
"BTable3.1_3", 
"BTable3.1_4",
"BTable3.1_5", 
"LTable3.1_1", 
"LTable3.1_2",
"LTable3.1_3", 
"LTable3.1_4",
"LTable3.1_5",
"STable3.1_1", 
"STable3.1_2", 
"STable3.1_3", 
"STable3.1_4", 
"STable3.1_5", 
"ATable3.1_1", 
"ATable3.1_2",
"ATable3.1_3", 
"ATable3.1_4",
"ATable3.1_5",

"BTable3.2_1",
"BTable3.2_2",
"BTable3.2_3",
"BTable3.2_4",
"BTable3.2_5",
"LTable3.2_1", 
"LTable3.2_2", 
"LTable3.2_3", 
"LTable3.2_4",
"LTable3.2_5",
"STable3.2_1",
"STable3.2_2", 
"STable3.2_3", 
"STable3.2_4", 
"STable3.2_5", 
"ATable3.2_1",
"ATable3.2_2",
"ATable3.2_3", 
"ATable3.2_4", 
"ATable3.2_5",

"BTable3.3_1",
"BTable3.3_2",
"BTable3.3_3",
"BTable3.3_4",
"BTable3.3_5", 
"LTable3.3_1", 
"LTable3.3_2",
"LTable3.3_3", 
"LTable3.3_4", 
"LTable3.3_5",
"STable3.3_1", 
"STable3.3_2", 
"STable3.3_3", 
"STable3.3_4", 
"STable3.3_5", 
"ATable3.3_1", 
"ATable3.3_2", 
"ATable3.3_3", 
"ATable3.3_4", 
"ATable3.3_5"
  ),
  fsim = rep(1,80))
}
```

"BTable3_1",
"BTable3_2", 
"BTable3_3", 
"BTable3_4", 
"BTable3_5",  
"LTable3_1",  
"LTable3_2", 
"LTable3_3", 
"LTable3_4", 
"LTable3_5",
"STable3_1", 
"STable3_2", 
"STable3_3", 
"STable3_4",  
"STable3_5",  
"ATable3_1",  
"ATable3_2", 
"ATable3_3", 
"ATable3_4", 
"ATable3_5",

"BTable3.1_1",
"BTable3.1_2",
"BTable3.1_3", 
"BTable3.1_4",
"BTable3.1_5", 
"LTable3.1_1", 
"LTable3.1_2",
"LTable3.1_3", 
"LTable3.1_4",
"LTable3.1_5",
"STable3.1_1", 
"STable3.1_2", 
"STable3.1_3", 
"STable3.1_4", 
"STable3.1_5", 
"ATable3.1_1", 
"ATable3.1_2",
"ATable3.1_3", 
"ATable3.1_4",
"ATable3.1_5",

"BTable3.2_1",
"BTable3.2_2",
"BTable3.2_3",
"BTable3.2_4",
"BTable3.2_5",
"LTable3.2_1", 
"LTable3.2_2", 
"LTable3.2_3", 
"LTable3.2_4",
"LTable3.2_5",
"STable3.2_1",
"STable3.2_2", 
"STable3.2_3", 
"STable3.2_4", 
"STable3.2_5", 
"ATable3.2_1",
"ATable3.2_2",
"ATable3.2_3", 
"ATable3.2_4", 
"ATable3.2_5",

"BTable3.3_1",
"BTable3.3_2",
"BTable3.3_3",
"BTable3.3_4",
"BTable3.3_5", 
"LTable3.3_1", 
"LTable3.3_2",
"LTable3.3_3", 
"LTable3.3_4", 
"LTable3.3_5",
"STable3.3_1", 
"STable3.3_2", 
"STable3.3_3", 
"STable3.3_4", 
"STable3.3_5", 
"ATable3.3_1", 
"ATable3.3_2", 
"ATable3.3_3", 
"ATable3.3_4", 
"ATable3.3_5"

Splitnonsplit test "SPLIT" sinatra sequential vs. parallel testing
```{r}
params <- if(HCRtoplot == "SPLIT"){list(
  scendir = c( #nonsplit
    "~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/spawbiotest_oldersinatra2bag/",
    "~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/spawbiotest_oldersinatra2all/",
  
    #split               
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2bag/sim1_10/",
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2bag/sim11_20/",
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2bag/sim21_30/",
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2bag/sim31_40/",
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2bag/sim41_50/",
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2all/sim1_10/",
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2all/sim11_20/",
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2all/sim21_30/",
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2all/sim31_40/",
"~/Desktop/FlounderMSE/kw_sims_test/TestingSims/testsims_old/SplittingSimsTest/runnewest50sims26years/split_oldersinatra2all/sim41_50/"
),
  scen.name = c(#1,2,3,4,5,6,7,8
"BNonsplit_bag",
"ANonsplit_all",
"BSplit_bag",
"BSplit_bag",
"BSplit_bag",
"BSplit_bag",
"BSplit_bag",
"ASplit_all",
"ASplit_all",
"ASplit_all",
"ASplit_all",
"ASplit_all"
  ),
  fsim = rep(1,12))
}
```

BBM "BBM"
```{r}
#BBM V2
params <- if(HCRtoplot == "BBMv2"){list(
  scendir = c("~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/1_bag/sim1_10/",
             "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.1/4_all/sim41_50/",
              
             "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/1_bag/sim1_10/",
             "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.2/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.3/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.4/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.5/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.6/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/Table3.7/4_all/sim41_50/"
              ),
  scen.name = c(
"BTable3_1", "BTable3_2", "BTable3_3", "BTable3_4", "BTable3_5",  "LTable3_1",  "LTable3_2", "LTable3_3", "LTable3_4", "LTable3_5",
"STable3_1", "STable3_2", "STable3_3",  "STable3_4",  "STable3_5",  "ATable3_1",  "ATable3_2", "ATable3_3", "ATable3_4", "ATable3_5",
"BTable3.1_1", "BTable3.1_2", "BTable3.1_3", "BTable3.1_4", "BTable3.1_5", "LTable3.1_1", "LTable3.1_2","LTable3.1_3", "LTable3.1_4","LTable3.1_5",
"STable3.1_1", "STable3.1_2", "STable3.1_3", "STable3.1_4", "STable3.1_5", "ATable3.1_1", "ATable3.1_2","ATable3.1_3", "ATable3.1_4","ATable3.1_5",
"BTable3.2_1","BTable3.2_2", "BTable3.2_3", "BTable3.2_4", "BTable3.2_5", "LTable3.2_1", "LTable3.2_2", "LTable3.2_3", "LTable3.2_4", "LTable3.2_5",
"STable3.2_1", "STable3.2_2", "STable3.2_3", "STable3.2_4", "STable3.2_5", "ATable3.2_1", "ATable3.2_2", "ATable3.2_3", "ATable3.2_4", "ATable3.2_5",
"BTable3.3_1","BTable3.3_2", "BTable3.3_3", "BTable3.3_4", "BTable3.3_5", "LTable3.3_1", "LTable3.3_2", "LTable3.3_3", "LTable3.3_4", "LTable3.3_5",
"STable3.3_1", "STable3.3_2", "STable3.3_3", "STable3.3_4", "STable3.3_5", "ATable3.3_1", "ATable3.3_2", "ATable3.3_3", "ATable3.3_4", "ATable3.3_5",
"BTable3.4_1","BTable3.4_2", "BTable3.4_3", "BTable3.4_4", "BTable3.4_5", "LTable3.4_1", "LTable3.4_2", "LTable3.4_3", "LTable3.4_4", "LTable3.4_5",
"STable3.4_1", "STable3.4_2", "STable3.4_3", "STable3.4_4", "STable3.4_5", "ATable3.4_1", "ATable3.4_2", "ATable3.4_3", "ATable3.4_4", "ATable3.4_5",
"BTable3.5_1","BTable3.5_2", "BTable3.5_3", "BTable3.5_4", "BTable3.5_5", "LTable3.5_1", "LTable3.5_2", "LTable3.5_3", "LTable3.5_4", "LTable3.5_5",
"STable3.5_1", "STable3.5_2", "STable3.5_3", "STable3.5_4", "STable3.5_5", "ATable3.5_1", "ATable3.5_2", "ATable3.5_3", "ATable3.5_4", "ATable3.5_5",
"BTable3.6_1", "BTable3.6_2", "BTable3.6_3", "BTable3.6_4", "BTable3.6_5", "LTable3.6_1", "LTable3.6_2", "LTable3.6_3", "LTable3.6_4", "LTable3.6_5",
"STable3.6_1", "STable3.6_2", "STable3.6_3", "STable3.6_4", "STable3.6_5", "ATable3.6_1", "ATable3.6_2", "ATable3.6_3", "ATable3.6_4", "ATable3.6_5",
"BTable3.7_1", "BTable3.7_2", "BTable3.7_3", "BTable3.7_4", "BTable3.7_5", "LTable3.7_1", "LTable3.7_2", "LTable3.7_3", "LTable3.7_4", "LTable3.7_5",
"STable3.7_1", "STable3.7_2", "STable3.7_3", "STable3.7_4", "STable3.7_5", "ATable3.7_1", "ATable3.7_2", "ATable3.7_3", "ATable3.7_4", "ATable3.7_5"
  ),
  fsim = rep(1,160))
}
```

BRP "BRP"
```{r}
params <- if(HCRtoplot == "BRP"){list(
  scendir = c("~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.1/4_all/sim41_50/",
              
             "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/1_bag/sim1_10/",
             "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.2/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.3/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.4/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.5/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.6/4_all/sim41_50/",
              
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/1_bag/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/1_bag/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/1_bag/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/1_bag/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/1_bag/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/2_length/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/2_length/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/2_length/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/2_length/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/2_length/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/3_season/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/3_season/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/3_season/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/3_season/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/3_season/sim41_50/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/4_all/sim1_10/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/4_all/sim11_20/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/4_all/sim21_30/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/4_all/sim31_40/",
              "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BRP/Table2.7/4_all/sim41_50/"
              ),
  scen.name = c(
"BTable3_1", "BTable3_2", "BTable3_3", "BTable3_4", "BTable3_5",  "LTable3_1",  "LTable3_2", "LTable3_3", "LTable3_4", "LTable3_5",
"STable3_1", "STable3_2", "STable3_3",  "STable3_4",  "STable3_5",  "ATable3_1",  "ATable3_2", "ATable3_3", "ATable3_4", "ATable3_5",
"BTable3.1_1", "BTable3.1_2", "BTable3.1_3", "BTable3.1_4", "BTable3.1_5", "LTable3.1_1", "LTable3.1_2","LTable3.1_3", "LTable3.1_4","LTable3.1_5",
"STable3.1_1", "STable3.1_2", "STable3.1_3", "STable3.1_4", "STable3.1_5", "ATable3.1_1", "ATable3.1_2","ATable3.1_3", "ATable3.1_4","ATable3.1_5",
"BTable3.2_1","BTable3.2_2", "BTable3.2_3", "BTable3.2_4", "BTable3.2_5", "LTable3.2_1", "LTable3.2_2", "LTable3.2_3", "LTable3.2_4", "LTable3.2_5",
"STable3.2_1", "STable3.2_2", "STable3.2_3", "STable3.2_4", "STable3.2_5", "ATable3.2_1", "ATable3.2_2", "ATable3.2_3", "ATable3.2_4", "ATable3.2_5",
"BTable3.3_1","BTable3.3_2", "BTable3.3_3", "BTable3.3_4", "BTable3.3_5", "LTable3.3_1", "LTable3.3_2", "LTable3.3_3", "LTable3.3_4", "LTable3.3_5",
"STable3.3_1", "STable3.3_2", "STable3.3_3", "STable3.3_4", "STable3.3_5", "ATable3.3_1", "ATable3.3_2", "ATable3.3_3", "ATable3.3_4", "ATable3.3_5",
"BTable3.4_1","BTable3.4_2", "BTable3.4_3", "BTable3.4_4", "BTable3.4_5", "LTable3.4_1", "LTable3.4_2", "LTable3.4_3", "LTable3.4_4", "LTable3.4_5",
"STable3.4_1", "STable3.4_2", "STable3.4_3", "STable3.4_4", "STable3.4_5", "ATable3.4_1", "ATable3.4_2", "ATable3.4_3", "ATable3.4_4", "ATable3.4_5",
"BTable3.5_1","BTable3.5_2", "BTable3.5_3", "BTable3.5_4", "BTable3.5_5", "LTable3.5_1", "LTable3.5_2", "LTable3.5_3", "LTable3.5_4", "LTable3.5_5",
"STable3.5_1", "STable3.5_2", "STable3.5_3", "STable3.5_4", "STable3.5_5", "ATable3.5_1", "ATable3.5_2", "ATable3.5_3", "ATable3.5_4", "ATable3.5_5",
"BTable3.6_1", "BTable3.6_2", "BTable3.6_3", "BTable3.6_4", "BTable3.6_5", "LTable3.6_1", "LTable3.6_2", "LTable3.6_3", "LTable3.6_4", "LTable3.6_5",
"STable3.6_1", "STable3.6_2", "STable3.6_3", "STable3.6_4", "STable3.6_5", "ATable3.6_1", "ATable3.6_2", "ATable3.6_3", "ATable3.6_4", "ATable3.6_5",
"BTable3.7_1", "BTable3.7_2", "BTable3.7_3", "BTable3.7_4", "BTable3.7_5", "LTable3.7_1", "LTable3.7_2", "LTable3.7_3", "LTable3.7_4", "LTable3.7_5",
"STable3.7_1", "STable3.7_2", "STable3.7_3", "STable3.7_4", "STable3.7_5", "ATable3.7_1", "ATable3.7_2", "ATable3.7_3", "ATable3.7_4", "ATable3.7_5"
  ),
  fsim = rep(1,160))
}
```

Organize Output
```{r}
#summarize the output files DONT RERUN THIS UNLESS NEEDED
all_results <- purrr::pmap_dfr(params,read_results, om.name=5)
```

```{r}
#View(all_results)
#generate time series of metrics
diag_ts <- get_diag_ts(all_results) %>% 
  mutate(nurow = ifelse(type == "spawning biomass" & value == 0,0,1),
         nurow = ifelse(type == "B/Bref" & value == 0,0,nurow)) %>% 
  filter(nurow==1) %>% 
  select(-nurow)
```

```{r}
#if you don't want to merge with external spreadsheet, and have selected the character name option, run this:

diag_ts <- diag_ts %>%
  mutate(RegType = ifelse( #edits start here
    substr(diag_ts$scenario, 1,1) == "B", "Bag",
    ifelse(
    substr(diag_ts$scenario, 1,1) == "L", "Length",
    ifelse(
    substr(diag_ts$scenario, 1,1) == "S", "Season",
    ifelse(
    substr(diag_ts$scenario, 1,1) == "A", "All", NA  
    )))))

#stack them if split into 5x10 -> this honestly might be redundant; results don't change 
diag_ts$isim <- ifelse(stringr::str_sub(diag_ts$scenario,-1) == "2",
                                             diag_ts$isim + 10, 
                       ifelse(stringr::str_sub(diag_ts$scenario,-1) == "3",
                                             diag_ts$isim + 20,
                              ifelse(stringr::str_sub(diag_ts$scenario,-1) == "4",
                                             diag_ts$isim + 30,
                                     ifelse(stringr::str_sub(diag_ts$scenario,-1) == "5",
                                             diag_ts$isim + 40, diag_ts$isim))))

#change these criteria as needed depending on scenario 
diag_ts$scenario <- ifelse(substr(diag_ts$scenario, 2,8) != "Table3.", "BBM",
                                   ifelse(substr(diag_ts$scenario, 2,9) == "Table3.1", "BRP",
                                   ifelse(substr(diag_ts$scenario, 2,9) == "Table3.2", "PCA",
                                   ifelse(substr(diag_ts$scenario, 2,9) == "Table3.3", "NCA",
                                  ifelse(substr(diag_ts$scenario, 2,9) == "Table3.4", "Table3.4",
                                    ifelse(substr(diag_ts$scenario, 2,9) == "Table3.5", "Table3.5",
                                    ifelse(substr(diag_ts$scenario, 2,9) == "Table3.6", "Table3.6",
                                   ifelse(substr(diag_ts$scenario, 2,9) == "Table3.7", "Table3.7", NA))))))))

 # View(diag_ts)
```

```{r}
# # time series plots
 p1 <- diag_ts %>% 
   filter(year != 2019) %>% 
   mutate(type = fct_relevel(type,c("spawning biomass", "total catch"))) %>% 
   filter(type %in% c("B/Bref","F/Fref"),
          scenario %in% c("MP 1","MP 2")) %>% 
   projection.plot()
```

```{r}
 ###### summarizing metrics

metrics <- diag_ts %>% 
  filter(year >= 2036) %>%   #2036 in original to get end of time series
  group_by(om, scenario, isim, 
         RegType, #for if using code, remove this if merging from spreadsheet 
           type) %>% 
  summarize(value = case_when(
    type == "F/Fref" ~ mean(value<1, na.rm=TRUE),
    type == "B/Bref" ~ mean(value>0.5, na.rm=TRUE),
    TRUE ~ mean(value, na.rm=TRUE)), .groups = "drop") %>% 
  distinct() %>%  #unsure what is happening, but this helps.
  rename(metric = type,
         mp = scenario) %>% 
  mutate(metric = case_when(
    metric == "F/Fref" ~ "not overfishing",
    metric == "B/Bref" ~ "not overfished",
    TRUE ~ metric))
#View(metrics)
median_metrics <- metrics %>% 
  group_by(om, mp, metric) %>% 
  summarize(value = median(value, na.rm=TRUE))
#################################################

#OR use this to read in a spreadsheet of scenario names and specs
scen_lookup <- read.csv("~/Downloads/scentable2next.csv") %>%
  janitor::clean_names() %>% rename(mp = run_number)
```

State Information
```{r}
### state information ###

read_state_results <- function(scendir = "~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/82824/BBM2/",scen.name="compare",
                               om.name = 1,
                         fsim = 1) {

recoutput2 <- read.table(paste0(scendir, "recoutput2.out"), header = FALSE, skip = 1) #TRUE)
nyrs <- length(unique(recoutput2[,2]))
nsim <- length(unique(recoutput2[,1]))
recoutput2[,1] <- rep(1:nsim, each = 10*nyrs)
names(recoutput2) <- c("isim","year","state","keep_num","rel_num","ntrips","nchoice","change_cs","cost",
                       "keep_one", "mulen_keep","mulen_release","trophy")
state_recoutput <- recoutput2 %>% 
  mutate(scenario = rep(scen.name,nrow(.)),
         isim = isim + fsim -1,
         om = rep(om.name,nrow(.)))

return(state_recoutput)
}


get_state_ts <- function(results) {
  
  diag_ts <- results %>% 
    mutate(#keep_to_rel = keep_num/release_num,
           change_cs = change_cs*-1,
           "kept per trip" = 1000*keep_num/ntrips,
           "rel per trip" = 1000*rel_num/ntrips,
           #"F/Fref" = frate/fmsy,
           #"B/Bref" = biomass/bmsy,
           "expense" = cost,
           cs_per_trip = change_cs/ntrips,
           #rec_removals = keep_wt + release_wt,
           keep_one = keep_one/ntrips)  %>% 
    select(scenario, isim, state, year, 
           #biomass, 
           #totcat_wt, 
           #rec_removals, 
           #keep_to_rel, 
           "kept per trip", #"F/Fref", "B/Bref",
           "rel per trip", 
           mulen_keep,
           mulen_release,
           trophy,
           expense,
           change_cs,
           ntrips,
           keep_one,
           cs_per_trip,
           #"kept:released"
           #prop_female
    ) %>% 
    # rename("spawning biomass" = biomass,
    #        "total catch" = totcat_wt,
    #        "kept:released" = keep_to_rel) %>% 
    pivot_longer(cols=c(#"spawning biomass","total catch","kept:released", 
                        "kept per trip", 
                        "rel per trip",
                        #"F/Fref", "B/Bref",
                        #rec_removals,
                        mulen_keep,
                        mulen_release,
                        trophy,
                        expense,
                        change_cs,
                        ntrips,
                        keep_one,
                        cs_per_trip,
                        #"kept:released"
                        #prop_female
    ),names_to = "type", values_to = "value") %>% 
    I()
  return(diag_ts)
}

#generate time series of state metrics
state_results <- purrr::pmap_dfr(params,read_state_results)

state_metrics <- get_state_ts(state_results) %>% 
  filter(state!=1) %>% 
  # mutate(nurow = ifelse(type == "spawning biomass" & value == 0,0,1),
  #        nurow = ifelse(type == "B/Bref" & value == 0,0,nurow)) %>% 
  # filter(nurow==1) %>% 
  # select(-nurow)
  filter(year >= 2036) %>%   #2036 in original
  group_by(scenario, type, isim, state) %>% 
  summarize(#value = case_when(
    # type == "F/Fref" ~ mean(value<1, na.rm=TRUE),
    # type == "B/Bref" ~ mean(value>0.5, na.rm=TRUE),
    #TRUE 
    value = mean(value, na.rm=TRUE), .groups = "drop") %>% 
  distinct() %>%  #unsure what is happening, but this helps.
  rename(metric = type,
         mp = scenario) #%>% 
  # mutate(metric = case_when(
  #   metric == "F/Fref" ~ "not overfishing",
  #   metric == "B/Bref" ~ "not overfished",
  #   TRUE ~ metric))

 state_metrics <- state_metrics %>% mutate(RegType = ifelse( #edits start here
    substr(state_metrics$mp, 1,1) == "B", "Bag",
    ifelse(
    substr(state_metrics$mp, 1,1) == "L", "Length",
    ifelse(
    substr(state_metrics$mp, 1,1) == "S", "Season",
    ifelse(
    substr(state_metrics$mp, 1,1) == "A", "All", NA  
    ))))) 
 
state_metrics$isim <- ifelse(stringr::str_sub(state_metrics$mp,-1) == "2",
                                             state_metrics$isim + 10, 
                       ifelse(stringr::str_sub(state_metrics$mp,-1) == "3",
                                             state_metrics$isim + 20,
                              ifelse(stringr::str_sub(state_metrics$mp,-1) == "4",
                                             state_metrics$isim + 30,
                                     ifelse(stringr::str_sub(state_metrics$mp,-1) == "5",
                                             state_metrics$isim + 40, state_metrics$isim))))


state_metrics$om <- 5.  #dummy value for 2024 rec measures modeling

```

Save Files
```{r}
saveRDS(metrics,"~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/101624/baseregsposter.rds")
saveRDS(median_metrics,"~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/101624/median_baseregsposter.rds")
#saveRDS(state_metrics,"~/Desktop/FlounderMSE/kw_sims_test/MSE_boxplots/82824/full_state_metricsBBMv2_#regchanged.rds") 
```

Make Plots
```{r}
# #metrics <- readRDS("all_results_distrib.rds")
# #median_metrics <- readRDS("all_results_medians.rds")
metrics <- readRDS("~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/101624/baseregsposter.rds")
median_metrics <- readRDS("~/Desktop/FlounderMSE/kw_sims_test/UnityOutput/101624/median_baseregsposter.rds")
state_metrics <- readRDS("~/Desktop/FlounderMSE/kw_sims_test/MSE_boxplots/82824/full_state_metricsBBMv2_regchanged.rds") %>%
  mutate(state = fct_relevel(state,
                             c("MA","RI","CT","NY","NJ","DE","MD","VA","NC")))

state_medians <- state_metrics %>% 
  group_by(om, mp, state, metric) %>% 
  summarize(value = median(value, na.rm=TRUE)) %>% 
  I()

#metrics3 <- rbind(metrics, metrics1)
#View(metrics3)

#prepare table for plotting 
metrics2 <- metrics %>% 
 # left_join(scen_lookup) %>% #include this if using sheet
  mutate(om = factor(om),
      #   om = fct_recode(om, "Base" = "1","MRIP Bias" = "2","Shift" = "3"),
         mp2 = fct_recode(factor(mp), #put hcr if using sheet, mp if using code in here
                          "BNonsplit_bag" = "BNonsplit_bag",
                          "BSplit_bag" = "BSplit_bag",
                           "ANonsplit_all" = "ANonsplit_all",
                          "ASplit_all" = "ASplit_all",
                       #   "PCA" = "PCA",
                       #   "BRP" = "BRP",
                       #   "BBM" = "BBM",
                       #   "NCA" = "NCA",
                          #   "Table3" = "Table3",
                       #  "Table3.1" = "Table3.1",
                       #  "Table3.2" = "Table3.2",
                       #  "Table3.3" = "Table3.3",
                      #   "Table3.4" = "Table3.4",
                      #  "Table3.5" = "Table3.5",
                     #    "Table3.6" = "Table3.6",
                     #    "Table3.7" = "Table3.7"
                        ),
       #  mp3 = fct_collapse(factor(RegType), #reg_to_change if sheet, RegType if not
       #              "Bag" = "Bag",
         #             "Length" = "Length",
            #             "Season" = "Season",
             #         "All" = "All"
             #        ),
   #     mp3 = fct_relevel(mp3, "bag", "season"),
         #value = ifelse(metric == "exp_keep", 0.39*value, value),
         metric = factor(metric, levels = c("keep_one",
                                            "kept per trip", #_mp1",
                                            "cs_per_trip",
                                            "trophy",
                                            #"keep_one_mp1",
                                            "keep_one_range", #_mp1",
                                            "kept:released", #_mp1",
                                            #"kept:rel_range", #_mp1",
                                            "not overfished",
                                            "not overfishing",
                                            "spawning biomass", #_mp1",
                                            "rel per trip", #_mp1",
                                            "rec_removals", #_mp1",
                                            "prop_female",
                                            "ntrips", #_mp1",
                                            "change_cs"#,
                                            #"exp_keep"
                                            #"gdp_mp1"
                                            ))) 

#View(metrics2)
```


```{r}
# add boxplots
p2 <- metrics2 %>% 
  drop_na() %>% 
  filter(!(metric %in% c("change_cs","keep_one_range"))) %>% 
  droplevels() %>% 
  #filter(om == "Base") %>% 
  ggplot() +
 # aes(x = mp3, y = value, fill = mp2) +
  aes(x = mp2, y = value, fill = mp2) +
  geom_boxplot(outlier.shape=NA) +
  scale_fill_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, scale = "free_y", drop = F) +
  ylab("performance metric value") +
  xlab("regulation to change") +
  theme_bw() +
  theme(legend.position = "bottom") + #,
        #axis.text.x = element_blank()) +
  labs(fill = "HCR") + #,
       #subtitle = "Base scenario") +
  guides(fill = guide_legend(nrow = 1))
# add table summaries
#ggsave("boxplot-metrics.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om2.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om3.png",p2,width=8,height=8)
#ggsave("boxplot-metrics.png",p2,width=9,height=6)
#ggsave("boxplot-metrics_estF.png",p2,width=9,height=6)
p2
```

(State-by-state stuff yet to be done for 2024 -> add in below at some point)

Put in organization for splitsims

```{r}
p3 <- median_metrics %>%  
   mutate(om = factor(om), 
          om = fct_recode(om, "Base" = "1","MRIP Bias" = "2","Shift" = "3")) %>%  
   mutate(mp = fct_recode(mp, 
                   "rhl" = "NCA",
                          "perc_change" = "PCA", 
                          "refpt" = "BRP",
                          "bmatrix" = "BBM")) %>%  
   #filter(!metric %in% c("change_cs", "cs_per_trip")) %>%  -->
   #filter(!metric %in% c("expense","cs_per_trip","total catch")) %>%  -->
   filter(metric %in% c("change_cs", "kept per trip", "kept:released", "not overfished", "not overfishing", "keep_one")) %>%  
   do_small_radar_plot()
```
